---
title: "Maps of maximum cross-correlation values"
author: "Letitia Ho"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/Users/letitiaho/src/talker_change_data_processing/4_permutation_test/")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("kableExtra")
```

```{r load_data, include=FALSE}
# Load data
source("../tools/functions.R")
original <- read.csv('data/original_maximum.csv')
shuffled <- read.csv('data/shuffled_maximum.csv')
```

```{r}
## Compute stats

# Number of permutations 
permutations <- 500

# Get coordinates for electrodes on map
coordinates <- get_layout()
```

####Overall tracking

```{r fig.width=6, fig.height=5}
shuffled_means <- aggregate(shuffled[,4:131], by=list(Category=shuffled$shuffle_number), FUN=mean)
original_means <- as.data.frame(t(apply(as.matrix(original[,3:131]), MARGIN = 2, mean)))
overall_proportions <- get_proportions_overall(shuffled_means, original_means)
overall_df <- data.frame(overall_proportions, coordinates)

# Map
plot <- ggplot() +
  geom_point(data = overall_df, aes(x = x, y = y, 
                                    size = 1/proportions, 
                                    alpha = 0.5,
                                    stroke = 0)) +
  geom_point(data = overall_df, aes(x = x, y = y, 
                                    size = 1,
                                    alpha = 0.5,
                                    stroke = 0)) + 
  scale_size_continuous(name = "p", breaks = c(20, 100, 200), labels = c("0.05", "0.01", "0.005")) +
  guides(alpha = FALSE) +
  ylim(0, 900) +
  xlim(0, 900) +
  annotate("text", x=20, y=5, label= "L", alpha = 0.8) +
  annotate("text", x=880, y=5, label= "R", alpha = 0.8) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        plot.background=element_blank())
plot
ggsave(plot = plot, filename = 'figs/overall.png', width = 6, height = 5)
```

####Tracking for each condition

```{r}
##Compute stats

# Compute significance of tracking each level for each channel
levels <- get_all_channel_proportions(shuffled, original)

# Compute significance of difference between levels in each condition for each channel
level_differences <- get_all_channel_proportions_differences(shuffled, original)

# Get list of channels
channels <- 1:128
```


```{r}
get_inverted_list <- function(channels, list) {
  inverted_list <- channels[!channels %in% list]
  return(inverted_list)
}

get_relevant_coords <- function(x, y, channels) {
  x <- x[channels]
  y <- y[channels]
  return(data.frame(x = x, y = y))
}

get_map <- function(df, channels, nodiff_channels, levels_label) {
  diff_coordinates <- get_relevant_coords(df$x, df$y, channels)
  nodiff_coordinates <- get_relevant_coords(df$x, df$y, nodiff_channels)
  
  ggplot() +
    geom_point(data = df, aes(x = x, y = y, 
                              size = 1/group1, 
                              colour = "#B8DE29FF",
                              alpha = 0.5,
                              stroke = 0)) +
    geom_point(data = df, aes(x = x, y = y, 
                              size = 1/group2,
                              colour = "#287D8EFF",
                              alpha = 0.5,
                              stroke = 0)) +
    geom_point(data = df, aes(x = 1000+x, y = y, 
                              size = 1/nodiff_group1, 
                              colour = "#B8DE29FF",
                              alpha = 0.5,
                              stroke = 0)) +
    geom_point(data = df, aes(x = 1000+x, y = y, 
                              size = 1/nodiff_group2,
                              colour = "#287D8EFF",
                              alpha = 0.5,
                              stroke = 0)) +
    geom_point(data = diff_coordinates, aes(x = x, y = y,
                                            size = 1,
                                            alpha = 0.5,
                                            stroke = 0)) +
    geom_point(data = nodiff_coordinates, aes(x = 1000+x, y = y,
                                              size = 1,
                                              alpha = 0.5,
                                              stroke = 0)) +
    scale_color_discrete(name = "Level", labels = levels_label) + 
    scale_size_continuous(name = "p", breaks = c(20, 100, 200), labels = c("0.05", "0.01", "0.005")) +
    guides(alpha = FALSE) +
    annotate("text", x=20, y=5, label= "L", alpha = 0.8) +
    annotate("text", x=880, y=5, label= "R", alpha = 0.8) +
    theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.background=element_blank(),
          panel.border=element_blank(),
          panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          plot.background=element_blank())
}
```


These maps depict the channels that show significantly different tracking between the two levels of each condition. The color of the point indicates the level that the channel shows significant tracking for, some channels significantly track both levels, some channels only track one. The size of the point is proportional to `1/p` and indicates how significant the tracking is. The larger the point, the more significant tracking in the channel. `p` was calculated as the proportion of resampled data with an average maximum cross-correlation more extreme than the observed average maximum cross-correlation value averaged across all participants for each condition level. (The smallest p-value was mapped from `0` to `1/502`, since there were only `502` resamplings Laplace's rule of succession was used to estimate the conservative probability of a more extreme value.)

**Talker**

```{r fig.height=5, fig.width=12}
# Identify channels that differentiate between same and different talker and channels that don't
talker_channels <- get_sig_channels(level_differences, "talker")
nodiff_talker_channels <- get_inverted_list(channels, talker_channels)

# Get p-values for tracking within each level
same_talker <- get_ps(levels, talker_channels, "same_talker", permutations)
different_talker <- get_ps(levels, talker_channels, "different_talker", permutations)
nodiff_same_talker <- get_ps(levels, nodiff_talker_channels, "same_talker", permutations)
nodiff_different_talker <- get_ps(levels, nodiff_talker_channels, "different_talker", permutations)

# Create data frame for bubbles
talker_df <- data.frame(group1 = same_talker, group2 = different_talker, nodiff_group1 = nodiff_same_talker, nodiff_group2 = nodiff_different_talker, coordinates)

# Plot
plot <- get_map(talker_df, talker_channels, nodiff_talker_channels, c("Same talker", "Different talker"))
plot
ggsave(plot = plot, filename = 'figs/talker.png', width = 12, height = 5)
```

**Meaning**

```{r fig.height=5, fig.width=12}
# Identify channels that differentiate between meaningful and nonsense
meaning_channels <- get_sig_channels(level_differences, "meaning")
nodiff_meaning_channels <- get_inverted_list(channels, meaning_channels)

# Get p-values for tracking within each level
meaningful <- get_ps(levels, meaning_channels, "meaningful", permutations)
nonsense <- get_ps(levels, meaning_channels, "nonsense", permutations)
nodiff_meaningful <- get_ps(levels, nodiff_meaning_channels, "meaningful", permutations)
nodiff_nonsense <- get_ps(levels, nodiff_meaning_channels, "nonsense", permutations)

# Create data frame for plotting
meaning_df <- data.frame(group1 = meaningful, group2 = nonsense, nodiff_group1 = nodiff_meaningful, nodiff_group2 = nodiff_nonsense, coordinates)

# Plot
plot <- get_map(meaning_df, meaning_channels, nodiff_meaning_channels, c("Meaningful", "Nonsense"))
plot
ggsave(plot = plot, filename = 'figs/meaning.png', width = 12, height = 5)
```

**Constraint**

```{r fig.height=5, fig.width=12}
# Identify channels that differentiate between low and high constraint
constraint_channels <- get_sig_channels(level_differences, "constraint")
nodiff_constraint_channels <- get_inverted_list(channels, constraint_channels)

# Get p-values for tracking within each level
low_constraint <- get_ps(levels, constraint_channels, "low_constraint", permutations)
high_constraint <- get_ps(levels, constraint_channels, "high_constraint", permutations)
nodiff_low <- get_ps(levels, nodiff_constraint_channels, "low_constraint", permutations)
nodiff_high <- get_ps(levels, nodiff_constraint_channels, "high_constraint", permutations)

# Create data frame for bubbles
constraint_df <- data.frame(group1 = low_constraint, group2 = high_constraint, nodiff_group1 = nodiff_low, nodiff_group2 = nodiff_high, coordinates)

# Plot
plot <- get_map(constraint_df, constraint_channels, nodiff_constraint_channels, c("Low constraint", "High constraint"))
plot
ggsave(plot = plot, filename = 'figs/constraint.png', width = 12, height = 5)
```