---
title: "Maps of maximum cross-correlation values"
author: "Letitia Ho"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/Users/letitiaho/src/talker_change_data_processing")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("kableExtra")
```

```{r load_data, include=FALSE}
source("src/tools/functions.R")
original <- read.csv('data/4_permutation_test/maximum.csv')
shuffled <- read.csv('data/4_permutation_test/shuffled_maximum.csv')
```

```{r}
# Get coordinates for electrodes on map
coordinates <- get_layout()

# Compute significance of tracking each level for each channel
levels <- get_all_channel_proportions(shuffled, original)

# Compute significance of difference between levels in each condition for each channel
level_differences <- get_all_channel_proportions_differences(shuffled, original)
```

```{r}
get_map <- function(df, levels_label) {
  ggplot() +
    geom_point(data = df, aes(x = x, y = y, 
                              size = 1/group1, 
                              colour = "#B8DE29FF",
                              alpha = 0.5,
                              stroke = 0)) +
    geom_point(data = df, aes(x = x, y = y, 
                              size = 1/group2,
                              colour = "#287D8EFF",
                              alpha = 0.5,
                              stroke = 0)) +
    geom_point(data = df, aes(x = x, y = y, 
                              size = 1,
                              alpha = 0.5,
                              stroke = 0)) + 
    scale_color_discrete(name = "Level", labels = levels_label) + 
    guides(size = FALSE, alpha = FALSE) +
    ylim(0, 900) +
    xlim(0, 900) +
    annotate("text", x=20, y=5, label= "L", alpha = 0.8) +
    annotate("text", x=880, y=5, label= "R", alpha = 0.8) +
    theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.background=element_blank(),
          panel.border=element_blank(),
          panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          plot.background=element_blank())
}
```


These maps depict the channels that show significantly different tracking between the two levels of each condition. The color of the point indicates the level that the channel shows significant tracking for, some channels significantly track both levels, some channels only track one. The size of the point is proportional to `1/p` and indicates how significant the tracking is. The larger the point, the more significant tracking in the channel. `p` was calculated as the proportion of resampled data with an average maximum cross-correlation more extreme than the observed average maximum cross-correlation value averaged across all participants for each condition level. (The smallest p-value was mapped from `0` to `1/210`, since there were only `208` resamplings Laplace's rule of succession was used to estimate the conservative probability of a more extreme value.)

**Talker**

```{r}
# Identify channels that differentiate between same and different talker
talker_channels <- get_sig_channels(level_differences, "talker")

# Get p-values for tracking within each level
same_talker <- get_ps(levels, talker_channels, "same_talker")
different_talker <- get_ps(levels, talker_channels, "different_talker")

# Create data frame for plotting
talker_df <- data.frame(group1 = same_talker, group2 = different_talker, coordinates)

# Plot
get_map(talker_df, c("Same talker", "Different talker"))
```

**Meaning**

```{r}
# Identify channels that differentiate between meaningful and nonsense
meaning_channels <- get_sig_channels(level_differences, "meaning")

# Get p-values for tracking within each level
meaningful <- get_ps(levels, meaning_channels, "meaningful")
nonsense <- get_ps(levels, meaning_channels, "nonsense")

# Create data frame for plotting
meaning_df <- data.frame(group1 = meaningful, group2 = nonsense, coordinates)

# Plot
get_map(meaning_df, c("Meaningful", "Nonsense"))
```

**Constraint**

```{r}
# Identify channels that differentiate between low and high constraint
constraint_channels <- get_sig_channels(level_differences, "constraint")

# Get p-values for tracking within each level
low_constraint <- get_ps(levels, constraint_channels, "low_constraint")
high_constraint <- get_ps(levels, constraint_channels, "high_constraint")

# Create data frame for plotting
constraint_df <- data.frame(group1 = low_constraint, group2 = high_constraint, coordinates)

# Plot
get_map(constraint_df, c("Low constraint", "High constraint"))
```