---
title: "Average"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_knit$set(root.dir = "/Users/letitiaho/src/talker_change_data_processing/")
setwd("/Users/letitiaho/src/talker_change_data_processing/")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("kableExtra")
source("tools/functions.R")
source("4_test_cross_correlations/src/functions.R")

# Param
ALT = 'greater' # 'greater' or 'two.sided'
```

```{r}
# Import data
xcorr <- read.csv(file = "3_cross_correlate/data/average.csv")
channels <- as.character(1:128)
```

#### One-sample t-tests for overall tracking

```{r}
overall <- get_subject_averages(xcorr)
overall_w <- get_one_sample_wilcoxon(overall, alt = ALT)

# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
overall_ps <- data.frame(channels, 'p'= overall_w$p)
map_df <- mutate_if(overall_ps, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1,
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x,
                                                                                 direction = 1,
                                                                                 begin = 0.65,
                                                                                 end = 1,
                                                                                 option = "B",
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "p")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```



#### One-sample wilcoxon for each condition

Compares the cross correlations for each condition level (e.g. same-talker, meaningful) to 0.

```{r}
# Data frames will be named according to their condition, with the code for talker, then meaning, then constraint listed in that order
# Same-talker = S
# Different-talker = T
# Meaningful = M
# Nonsense = N
# Low constraint = L
# High constraint = H
S <- subset(xcorr, talker = "S") %>% get_subject_averages()
T <- subset(xcorr, talker = "T") %>% get_subject_averages()
M <- subset(xcorr, meaning = "M") %>% get_subject_averages()
N <- subset(xcorr, meaning = "N") %>% get_subject_averages()
L <- subset(xcorr, constraint = "L") %>% get_subject_averages()
H <- subset(xcorr, constraint = "H") %>% get_subject_averages()
```

```{r}
S_w <- get_one_sample_wilcoxon(S, ALT)
T_w <- get_one_sample_wilcoxon(T, ALT)
M_w <- get_one_sample_wilcoxon(M, ALT)
N_w <- get_one_sample_wilcoxon(N, ALT)
L_w <- get_one_sample_wilcoxon(L, ALT)
H_w <- get_one_sample_wilcoxon(H, ALT)
```

```{r}
# Creating a table to display all the p-values
one_sample_w <- data.frame(channels, 
                     'S' = S_w$p,
                     'T' = T_w$p, 
                     'M' = M_w$p,
                     'N' = N_w$p, 
                     'L' = L_w$p,
                     'H' = H_w$p)
map_df <- mutate_if(one_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "S", "T", "M", "N", "S", "G")) %>%
  add_header_above(c(" " = 1, "Talker" = 2, "Meaning" = 2, "Constraint" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```


```{r}
sum(overall_w$p < 0.05)
sum(T_w$p < 0.05)
sum(S_w$p < 0.05)
sum(M_w$p < 0.05)
sum(N_w$p < 0.05)
sum(L_w$p < 0.05)
sum(H_w$p < 0.05)
```

#### Two-sample Wilcoxon

Compares cross correlations between the two levels of each condition. 

```{r}
talker_w <- get_two_sample_wilcoxon(S, T)
meaning_w <- get_two_sample_wilcoxon(M, N)
constraint_w <- get_two_sample_wilcoxon(L, H)
```

```{r}
# Creating a table to display all the p-values
two_sample_w <- data.frame(channels, 
                     'talker' = talker_w$p,
                     'meaning' = meaning_w$p,
                     'constraint' = constraint_w$p)
map_df <-  mutate_if(two_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "Talker", "Meaning", "Constraint")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
sum(talker_w$p < 0.05)
sum(meaning_w$p < 0.05)
sum(constraint_w$p < 0.05)
```


#### Wilcoxon with interaction by constraint

```{r}
# Subset talker
SL <- subset(xcorr, talker = "S", constraint = "L") %>% get_subject_averages()
SH <- subset(xcorr, talker = "S", constraint = "H") %>% get_subject_averages()
TL <- subset(xcorr, talker = "T", constraint = "L") %>% get_subject_averages()
TH <- subset(xcorr, talker = "T", constraint = "H") %>% get_subject_averages()

# Subset meaning
ML <- subset(xcorr, meaning = "M", constraint = "L") %>% get_subject_averages()
MH <- subset(xcorr, meaning = "M", constraint = "H") %>% get_subject_averages()
NL <- subset(xcorr, meaning = "N", constraint = "L") %>% get_subject_averages()
NH <- subset(xcorr, meaning = "N", constraint = "H") %>% get_subject_averages()
```

```{r}
# One-sample t-tests for talker
SL_w <- get_one_sample_wilcoxon(SL, ALT)
SH_w <- get_one_sample_wilcoxon(SH, ALT)
TL_w <- get_one_sample_wilcoxon(TL, ALT)
TH_w <- get_one_sample_wilcoxon(TH, ALT)

# One-sample t-tests for meaning
ML_w <- get_one_sample_wilcoxon(ML, ALT)
MH_w <- get_one_sample_wilcoxon(MH, ALT)
NL_w <- get_one_sample_wilcoxon(NL, ALT)
NH_w <- get_one_sample_wilcoxon(NH, ALT)
```

```{r}
# Creating a table to display all the p-values
interaction_w <- data.frame(channels, 
                     'SL' = SL_w$p,
                     'SH' = SH_w$p,
                     'TL' = TL_w$p,
                     'TH' = TH_w$p, 
                     'ML' = ML_w$p,
                     'MH' = MH_w$p,
                     'NL' = NL_w$p,
                     'NH' = NH_w$p)
map_df <- mutate_if(interaction_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "L", "H", "L", "H", "L", "H", "L", "H")) %>%
  add_header_above(c(" " = 1, "Same-talker" = 2, "Different-talker" = 2, "Meaningful" = 2, "Nonsense" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
talker_L_w <- get_two_sample_wilcoxon(SL, TL)
talker_H_w <- get_two_sample_wilcoxon(SH, TH)
meaning_L_w <- get_two_sample_wilcoxon(ML, NL)
meaning_H_w <- get_two_sample_wilcoxon(MH, NH)
```

```{r}
# Creating a table to display all the p-values
interaction_two_sample_w <- data.frame(channels, 
                     'talker_L' = talker_L_w$p,
                     'talker_H' = talker_H_w$p,
                     'meaning_L' = meaning_L_w$p,
                     'meaning_H' = meaning_H_w$p)
map_df <- mutate_if(interaction_two_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "L", "H", "L", "H")) %>%
  add_header_above(c(" " = 1, "Talker" = 2, "Meaning" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

#### T-tests against difference set by low vs high-constraint sentences

```{r}
# SML <- subset(xcorr, talker = "S", meaning = "M", constraint = "L", keepLabels = T)
# SML_means <- aggregate(SML[,2:129], by=list(SML$subject_number), FUN=mean) %>%
#   subset(-1)
```

```{r}
# take meaningful and same-talker sentences and compare correlations of low- vs high-constraint sentences
# compare this difference to meaningful and high-constraint same- vs different-talker sentences
# compare this difference to same-talker and high-constraint meaningful vs nonsense sentences
# SML <- subset(xcorr, talker = "S", meaning = "M", constraint = "L", keepLabels = TRUE)
# SML_means <- aggregate(SML[,5:132], by=list(SML$subject_number), FUN=mean) %>% select(-"Group.1")
# SMH <- subset(xcorr, talker = "S", meaning = "M", constraint = "H", keepLabels = TRUE) 
# SMH_means <- aggregate(SMH[,5:132], by=list(SMH$subject_number), FUN=mean) %>% select(-"Group.1")
# baseline <- SMH_means - SML_means
# 
# TMH <- subset(xcorr, talker = "T", meaning = "M", constraint = "H", keepLabels = TRUE)
# TMH_means <- aggregate(TMH[,5:132], by=list(TMH$subject_number), FUN=mean) %>% select(-"Group.1")
# talker_compare <- TMH_means - SMH_means
# 
# SNH <- subset(xcorr, talker = "S", meaning = "N", constraint = "H", keepLabels = TRUE)
# SNH_means <- aggregate(SNH[,5:132], by=list(SNH$subject_number), FUN=mean) %>% select(-"Group.1")
# meaning_compare <- SNH_means - SMH_means
```

```{r}
# t-test by subject
# talker_compare_w <- get_two_sample_wilcoxon(baseline, talker_compare)
# meaning_compare_w <- get_two_sample_wilcoxon(baseline, meaning_compare)
```

```{r}
# Creating a table to display all the p-values
# compare_w <- data.frame(channels, 
#                      'talker' = talker_compare_w$p,
#                      'meaning' = meaning_compare_w$p)
# map_df <- mutate_if(compare_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
#   mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
#                                             cell_spec(x, NULL),
#                                             cell_spec(x, background = spec_color(x, 
#                                                                                  direction = 1, 
#                                                                                  begin = 0.65, 
#                                                                                  end = 1, 
#                                                                                  option = "B", 
#                                                                                  scale_from = c(0,0.1))))})
# 
# kable(map_df, escape = F, col.names = c("Channel", "Talker", "Meaning")) %>%
#   kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
# save(overall_w, one_sample_w, two_sample_w, interaction_w, interaction_two_sample_w, file = "8_wilcoxon/data/one-sided_wilcoxon_results.RData")
fname = paste("4_test_cross_correlations/data/", ALT, "_wilcoxon_results.RData", sep = "")
save(overall_w, S_w, T_w, M_w, N_w, L_w, H_w, talker_w, meaning_w, constraint_w, SH_w, SL_w, TH_w, TL_w, file = fname)
```

