---
title: "Average"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_knit$set(root.dir = "/Users/letitiaho/src/talker_change_data_processing/")
setwd("/Users/letitiaho/src/talker_change_data_processing/")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("kableExtra")
library("tidyr")
source("tools/functions.R")
source("4_test_cross_correlations/src/functions.R")

# Param
ALT = 'two.sided' # 'greater' or 'two.sided'
NORM = "normalized_" # either "normalized_" or ""
```

```{r}
# Import data
xcorr <- read.csv(file = paste("3_cross_correlate/data/", NORM, "average.csv", sep = ''))
channels <- as.character(1:128)
subs <- as.character(unique(xcorr$subject_number))
n <- length(subs)
conds <- unique(c(xcorr$constraint, xcorr$meaning, xcorr$talker))
```

```{r}
channel_labels <- paste("X", as.character(1:128), sep = "")

standardize_ws <- function(p, w) {
  i <- which(p == max(p))
  mid <- w[i]
  w_adjusted <- abs(w - mid)
  return(w_adjusted)
}

get_critical_value <- function(p, w) {
  c <- min(w[which(p < 0.05)])
  return(c)
}

plot_ws <- function(w1, w2, labs, c, fname) {
  df_long <- data.frame(w1 = unlist(w1), w2 = unlist(w2)) %>%
    pivot_longer(cols = c("w1", "w2"),
                 names_to = "condition",
                 values_to = "W")
  p <- ggplot(df_long, aes(x = W, fill = condition)) +
    geom_histogram(position ="identity", alpha=0.65, bins = 15) +
    geom_vline(xintercept = c) +
    scale_fill_discrete(labels = labs) +
    scale_color_discrete(labels = labs) +
    ylim(c(0, 25)) +
    xlim(c(0, 35))
  ggsave(p, filename = fname, width = 12, height = 7)
  return(p)
}
```


#### One-sample t-tests for overall tracking

```{r}
overall <- get_subject_averages(xcorr)
overall_w <- get_one_sample_wilcoxon_for_each_channel(overall, alt = ALT)

# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
overall_ps <- data.frame(channels, 'p'= overall_w$p)
map_df <- mutate_if(overall_ps, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1,
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x,
                                                                                 direction = 1,
                                                                                 begin = 0.65,
                                                                                 end = 1,
                                                                                 option = "B",
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "p")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
# Get baseline
baseline <- overall %>%
  summarise_at(vars(all_of(channel_labels)), mean, na.rm = TRUE) %>%
  select(all_of(channel_labels)) %>%
  as.numeric()
```



#### One-sample wilcoxon for each condition

Compares the cross correlations for each condition level (e.g. same-talker, meaningful) to 0.

```{r}
get_one_sample_wilcoxon_for_each_channel_against_baseline <- function(data, alt = 'greater', baseline = 0) {
  w <- mapply(function(x, y) {wilcox.test(x, exact = TRUE, mu = y)$statistic}, data, baseline)
  p <- mapply(function(x, y) {wilcox.test(x, exact = TRUE, mu = y)$p.value}, data, baseline)
  return(data.frame("w" = w, "p" = p))
}
```

```{r}
# Data frames will be named according to their condition, with the code for talker, then meaning, then constraint listed in that order
# Same-talker = S
# Different-talker = T
# Meaningful = M
# Nonsense = N
# Low constraint = L
# High constraint = H
S <- subset(xcorr, talker = "S") %>% get_subject_averages()
T <- subset(xcorr, talker = "T") %>% get_subject_averages()
M <- subset(xcorr, meaning = "M") %>% get_subject_averages()
N <- subset(xcorr, meaning = "N") %>% get_subject_averages()
L <- subset(xcorr, constraint = "L") %>% get_subject_averages()
H <- subset(xcorr, constraint = "H") %>% get_subject_averages()
```

```{r}
S_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(S, ALT, baseline)
T_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(T, ALT, baseline)
M_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(M, ALT, baseline)
N_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(N, ALT, baseline)
L_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(L, ALT, baseline)
H_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(H, ALT, baseline)

# S_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(S, ALT)
# T_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(T, ALT)
# M_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(M, ALT)
# N_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(N, ALT)
# L_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(L, ALT)
# H_w <- get_one_sample_wilcoxon_for_each_channel_against_baseline(H, ALT)
```

```{r}
# Creating a table to display all the p-values
one_sample_w <- data.frame(channels, 
                     'S' = S_w$p,
                     'T' = T_w$p, 
                     'M' = M_w$p,
                     'N' = N_w$p, 
                     'L' = L_w$p,
                     'H' = H_w$p)
map_df <- mutate_if(one_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "S", "T", "M", "N", "S", "G")) %>%
  add_header_above(c(" " = 1, "Talker" = 2, "Meaning" = 2, "Constraint" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```


```{r}
sum(overall_w$p < 0.05)
sum(T_w$p < 0.05)
sum(S_w$p < 0.05)
sum(M_w$p < 0.05)
sum(N_w$p < 0.05)
sum(L_w$p < 0.05)
sum(H_w$p < 0.05)
```

#### Two-sample Wilcoxon

Compares cross correlations between the two levels of each condition. 

```{r}
talker_w <- get_two_sample_wilcoxon_for_each_channel(S, T, paired = TRUE)
meaning_w <- get_two_sample_wilcoxon_for_each_channel(M, N, paired = TRUE)
constraint_w <- get_two_sample_wilcoxon_for_each_channel(L, H, paired = TRUE)

talker_w$w_adjusted <-standardize_ws(talker_w$p, talker_w$w)
meaning_w$w_adjusted <-standardize_ws(meaning_w$p, meaning_w$w)
constraint_w$w_adjusted <-standardize_ws(constraint_w$p, constraint_w$w)
```

```{r}
# Creating a table to display all the p-values
two_sample_w <- data.frame(channels, 
                     'talker' = talker_w$p,
                     'meaning' = meaning_w$p,
                     'constraint' = constraint_w$p)
map_df <-  mutate_if(two_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "Talker", "Meaning", "Constraint")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
sum(talker_w$p < 0.05)
sum(meaning_w$p < 0.05)
sum(constraint_w$p < 0.05)
```

#### Plot test statistics

```{r}
# Plot p-values
hist(S_w$p, ylim = c(0,40))
hist(T_w$p, ylim = c(0,40))
hist(M_w$p, ylim = c(0,40))
hist(N_w$p, ylim = c(0,40))
hist(L_w$p, ylim = c(0,40))
hist(H_w$p, ylim = c(0,40))
```

```{r}
# Plot test statistics
overall_w$w_adjusted <- standardize_ws(overall_w$p, overall_w$w)
S_w$w_adjusted <- standardize_ws(S_w$p, S_w$w)
T_w$w_adjusted <- standardize_ws(T_w$p, T_w$w)
M_w$w_adjusted <- standardize_ws(M_w$p, M_w$w)
N_w$w_adjusted <- standardize_ws(N_w$p, N_w$w)
L_w$w_adjusted <- standardize_ws(L_w$p, L_w$w)
H_w$w_adjusted <- standardize_ws(H_w$p, H_w$w)

c <- get_critical_value(S_w$p, S_w$w_adjusted)
plot_ws(T_w$w_adjusted, S_w$w_adjusted, c("T", "S"), c, "4_test_cross_correlations/figs/ws_talker_poster.png")
plot_ws(N_w$w_adjusted, M_w$w_adjusted, c("N", "M"), c, "4_test_cross_correlations/figs/ws_meaning_poster.png")
plot_ws(H_w$w_adjusted, L_w$w_adjusted, c("H", "L"), c, "4_test_cross_correlations/figs/ws_constraint_poster.png")
```

```{r}
p <- ggplot(overall_w, aes(x = w_adjusted)) +
    geom_histogram(position ="identity", alpha=0.8, bins = 15) +
    geom_vline(xintercept = c) +
    scale_fill_discrete(labels = labs) +
    scale_color_discrete(labels = labs) +
    ylim(c(0, 25)) +
    xlim(c(0, 35)) +
    xlab("w")
p 
# ggsave(filename = "4_test_cross_correlations/figs/ws_overall_poster.png", plot = p, width = 6, height = 2.5)
sum(overall_w$p < 0.05)
```


#### Plot cross correlations

```{r}
# Plot cross correlations for channels with significant cross correlations

get_sig_xcorrs <- function(xcorr, p) { # get xcorrs from sig channels
  sig_xcorr <- as.matrix(xcorr) %>%
   .[, which(p < 0.05)] %>%
    abs() %>%
    rowMeans() %>% # colMeans() compares channels, rowMeans() compares subs
    remove_outliers()
  return(sig_xcorr)
}

get_sig_xcorrs_df <- function(condition, group, sig_xcorr) {
  condition_col <- rep(condition, length(sig_xcorr))
  group_col <- rep(group, length(sig_xcorr))
  df <- data.frame(condition, sig_xcorr, group)
}

remove_outliers <- function(x) {
  x <- x[!x %in% boxplot.stats(x)$out]
  return(x)
}

S_sig <- get_sig_xcorrs(S, S_w$p)
T_sig <- get_sig_xcorrs(T, T_w$p)
M_sig <- get_sig_xcorrs(M, M_w$p)
N_sig <- get_sig_xcorrs(N, N_w$p)
L_sig <- get_sig_xcorrs(L, L_w$p)
H_sig <- get_sig_xcorrs(H, H_w$p)

# ggsave(p, filename = '4_test_cross_correlations/figs/xcorrs_for_sig_channels_poster_2.png', width = 10, height = 5)
```

```{r}
df_talker <- get_sig_xcorrs_df('S', 'talker', S_sig) %>%
  rbind(get_sig_xcorrs_df('T', 'talker', T_sig))
df_meaning <- rbind(get_sig_xcorrs_df('M', 'meaning', M_sig)) %>%
  rbind(get_sig_xcorrs_df('N', 'meaning', N_sig))
df_constraint <- rbind(get_sig_xcorrs_df('L', 'constraint', L_sig)) %>%
  rbind(get_sig_xcorrs_df('H', 'constraint', H_sig))

# New facet label names for condition variable
# condition.labs <- c("S", "T", "M", "N", "L", "H")

p_talker <- ggplot(df_talker, aes(x = condition, y = sig_xcorr, fill = group)) +
  geom_boxplot(fill = "#026fa1") +
  geom_signif(comparisons = list(c("S", "T")), annotations = '*') +
  ylim(c(0.5e-05, 6e-05)) +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") +
  xlab('Talker')
p_meaning <- ggplot(df_meaning, aes(x = condition, y = sig_xcorr, fill = group)) +
  geom_boxplot(fill = "#048fcf") +
  geom_signif(comparisons = list(c("M", "N")), map_signif_level = TRUE) +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") +
  ylim(c(0.5e-05, 6e-05)) +
  xlab('Meaning')
p_constraint <- ggplot(df_constraint, aes(x = condition, y = sig_xcorr, fill = group)) +
  geom_boxplot(fill = "#09a6ed") +
  theme(legend.position = "none") +
  ylim(c(0.5e-05, 6e-05)) +
  xlab('Constraint') +
  ylab("cross correlations") 
p <- ggarrange(p_constraint, p_meaning, p_talker, ncol = 3)
  
p
# getwd()
# ggsave(p, filename = '4_test_cross_correlations/figs/xcorrs_for_sig_channels_poster_3.png', width = 8, height = 4)
```



#### Get stats

```{r}
# one-sample t-test
overall_sig <- get_sig_xcorrs(overall, overall_w$p)
t.test(overall_sig)

# t-tests between levels 
t.test(T_sig, S_sig)
t.test(M_sig, N_sig)
t.test(L_sig, H_sig)
```

## Count the number of channels tracking each condition level

```{r warning=FALSE}
count_sig_chans <- function(xcorr, subs, ALT, talker = NaN, meaning = NaN, constraint = NaN) {
  cond_xcorr <- subset(xcorr,  talker = talker, meaning = meaning, constraint = constraint)
  counts <- c()
  for (sub in subs) {
    sub_xcorr <- cond_xcorr[cond_xcorr$subject_number == sub,]
    ws <- get_one_sample_wilcoxon_for_each_channel(sub_xcorr, alt = ALT)
    count <- sum(ws$p < 0.05)
    counts <- c(counts, count)
  }
  counts <- remove_outliers(counts)
  return(counts)
}

S_counts <- count_sig_chans(xcorr, subs, ALT, talker = "S")
T_counts <- count_sig_chans(xcorr, subs, ALT, talker = "T")
M_counts <- count_sig_chans(xcorr, subs, ALT, meaning = "M")
N_counts <- count_sig_chans(xcorr, subs, ALT, meaning = "N")
L_counts <- count_sig_chans(xcorr, subs, ALT, constraint = "L")
H_counts <- count_sig_chans(xcorr, subs, ALT, constraint = "H")
```

```{r warning=FALSE}
overall_counts <- count_sig_chans(xcorr, subs, ALT)
t.test(overall_counts)
```


#### Get stats

```{r}
# For talker
print(paste("Mean channel counts for same-talker: ", round(mean(S_counts), 3), sep = ''))
print(paste("sd: ", round(sd(S_counts), 3), sep = ''))
print(paste("Mean channel counts for different-talker: ", round(mean(T_counts), 3), sep = ''))
print(paste("sd: ", round(sd(T_counts), 3), sep = ''))
t.test(S_counts, T_counts)

# For meaning
print(paste("Mean channel counts for meaningful sentences: ", round(mean(M_counts), 3), sep = ''))
print(paste("sd: ", round(sd(M_counts), 3), sep = ''))
print(paste("Mean channel counts for nonsense sentences: ", round(mean(N_counts), 3), sep = ''))
print(paste("sd: ", round(sd(N_counts), 3), sep = ''))
t.test(M_counts, N_counts)

# For constraint
print(paste("Mean channel counts for low constraint sentences: ", round(mean(L_counts), 3), sep = ''))
print(paste("sd: ", round(sd(L_counts), 3), sep = ''))
print(paste("Mean channel counts for high constraint sentences: ", round(mean(H_counts), 3), sep = ''))
print(paste("sd: ", round(sd(H_counts), 3), sep = ''))
t.test(L_counts, H_counts)
```

#### Plot

```{r}
# p_talker <- ggplot(df_talker, aes(x = condition, y = sig_xcorr, fill = group)) +
#   geom_boxplot(fill = "#09a6ed") +
#   geom_signif(comparisons = list(c("S", "T")), annotations = '*') +
#   ylab("cross correlations") +
#   ylim(c(0.5e-05, 6e-05)) +
#   theme(legend.position = "none") +
#   xlab('Talker')
# p_meaning <- ggplot(df_meaning, aes(x = condition, y = sig_xcorr, fill = group)) +
#   geom_boxplot(fill = "#048fcf") +
#   geom_signif(comparisons = list(c("M", "N")), map_signif_level = TRUE) +
#   theme(axis.text.y=element_blank(),
#         axis.ticks.y=element_blank(),
#         axis.title.y =element_blank(),
#         legend.position = "none") +
#   ylim(c(0.5e-05, 6e-05)) +
#   xlab('Meaning')
# p_constraint <- ggplot(df_constraint, aes(x = condition, y = sig_xcorr, fill = group)) +
#   geom_boxplot(fill = "#026fa1") +
#   theme(axis.text.y=element_blank(),
#         axis.ticks.y=element_blank(),
#         axis.title.y =element_blank(),
#         legend.position = "none") +
#   ylim(c(0.5e-05, 6e-05)) +
#   xlab('Constraint')
# p <- ggarrange(p_talker, p_meaning, p_constraint, ncol = 3)
# 
# 


df_talker <- data.frame(cond = rep('Same', length(S_counts)), group = rep('talker', length(S_counts)), counts = S_counts) %>%
  rbind(data.frame(cond = rep('Different', length(T_counts)), group = rep('talker', length(T_counts)), counts = T_counts)) 
df_meaning <- data.frame(cond = rep('Meaningful', length(M_counts)), group = rep('meaning', length(M_counts)), counts = M_counts) %>%
  rbind(data.frame(cond = rep('Nonsense', length(N_counts)), group = rep('meaning', length(N_counts)), counts = N_counts)) 
df_constraint <- data.frame(cond = rep('Low', length(L_counts)), group = rep('constraint', length(L_counts)), counts = L_counts) %>%
  rbind(data.frame(cond = rep('High', length(H_counts)), group = rep('constraint', length(H_counts)), counts = H_counts))

p_constraint <- ggplot(df_constraint, aes(x = cond, y = counts, fill = group)) + 
  geom_boxplot() +
  geom_boxplot(fill = "#09a6ed") +
  theme(legend.position = "none") +
  ylim(c(0, 45)) +
  ylab("channels") +
  xlab('Constraint')
p_meaning <- ggplot(df_meaning, aes(x = cond, y = counts, fill = group)) + 
  geom_boxplot() +
  geom_boxplot(fill = "#048fcf") +
  # geom_signif(comparisons = list(c("M" , "N")), map_signif_level = TRUE) +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") + 
  ylim(c(0, 45)) +
  ylab("channels") +
  xlab('Meaning')
p_talker <- ggplot(df_talker, aes(x = cond, y = counts, fill = group)) + 
  geom_boxplot() +
  geom_boxplot(fill = "#026fa1") +
  geom_signif(comparisons = list(c("Same", "Different")), annotations = "*", map_signif_level = TRUE) +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") +
  ylim(c(0, 45)) +
  ylab("channels") +
  xlab('Talker')
p <- ggarrange(p_constraint, p_meaning, p_talker, ncol = 3, widths = c(2, 1.8, 1.8))
p
# ggsave(p, filename = '4_test_cross_correlations/figs/compare_channel_counts_poster.png', width = 8, height = 4)
```
## Count the number of channels tracking each condition

```{r warning=FALSE}
# Count the number of channels tracking each condition for each subject

count_sig_chans_two_samp <- function(xcorr, subs, cond) {
  if (cond == "talker" ) {
    cond_xcorr_1 <- subset(xcorr,  talker = "S")
    cond_xcorr_2 <- subset(xcorr,  talker = "T")
  } else if (cond == "meaning" ) {
    cond_xcorr_1 <- subset(xcorr,  meaning = "M")
    cond_xcorr_2 <- subset(xcorr,  meaning = "N")
  } else if (cond == "constraint") {
    cond_xcorr_1 <- subset(xcorr,  constraint = "L")
    cond_xcorr_2 <- subset(xcorr,  constraint = "H")
  }

  counts <- c()
  for (sub in subs) {
    if (sub == '302') {
      next
    }
    print(sub)
    sub_xcorr_1 <- cond_xcorr_1[cond_xcorr_1$subject_number == sub,]
    sub_xcorr_2 <- cond_xcorr_2[cond_xcorr_1$subject_number == sub,]
    ws <- get_two_sample_wilcoxon_for_each_channel(sub_xcorr_1, sub_xcorr_2, paired = FALSE)
    count <- sum(ws$p < 0.05, na.rm = TRUE)
    print(count)
    counts <- c(counts, count)
  }
  counts <- remove_outliers(counts)
  return(counts)
}

talker_counts <- count_sig_chans_two_samp(xcorr, subs, "talker")
meaning_counts <- count_sig_chans_two_samp(xcorr, subs, "meaning")
constraint_counts <- count_sig_chans_two_samp(xcorr, subs, "constraint")

# save(talker_counts, meaning_counts, constraint_counts, file = '../data/cond_channel_counts.RData')
```

#### Get stats

```{r}
df <- data.frame(cond = rep('talker', length(talker_counts)), counts = talker_counts) %>%
  rbind(data.frame(cond = rep('meaning', length(meaning_counts)), counts = meaning_counts)) %>%
  rbind(data.frame(cond = rep('constraint', length(constraint_counts)), counts = constraint_counts))

print(paste("Mean channel counts for talker: ", round(mean(talker_counts), 3), sep = ''))
print(paste("sd: ", round(sd(talker_counts), 3), sep = ''))
print(paste("Mean channel counts for meaning: ", round(mean(meaning_counts), 3), sep = ''))
print(paste("sd: ", round(sd(meaning_counts), 3), sep = ''))
print(paste("Mean channel counts for constraint: ", round(mean(constraint_counts), 3), sep = ''))
print(paste("sd: ", round(sd(constraint_counts), 3), sep = ''))

fit <- aov(counts ~ cond, data = df)
summary(fit)
TukeyHSD(fit)
```

#### Plot

```{r}
p <- ggplot(df, aes(x = cond, y = counts, fill = cond)) +
  geom_boxplot() +
  scale_fill_manual(values=c("#09a6ed", "#048fcf", "#026fa1")) +
  # scale_fill_brewer(palette="Blues") +
  geom_signif(comparisons = list(c("talker", "constraint")), 
                                 map_signif_level = TRUE,
                                 annotations = c("*")) +
    theme(legend.position = "none") +
  ylab("channels") +
  ylim(c(0, 45)) +
  xlab("")
p
# ggsave(p, filename = '4_test_cross_correlations/figs/compare_condition_channel_counts_poster.png', width = 8, height = 4)
```
#### Save everything

```{r}
# getwd()
# fname = paste("4_test_cross_correlations/data/", NORM, ALT, "_wilcoxon_results.RData", sep = "")
# save(overall_w, 
#      S_w, 
#      T_w, 
#      M_w, 
#      N_w, 
#      L_w, 
#      H_w, 
#      talker_w, 
#      meaning_w, 
#      constraint_w, 
#      talker_L_w, 
#      talker_H_w, 
#      meaning_L_w,
#      meaning_H_w,
#      SH_w, 
#      SL_w, 
#      TH_w, 
#      TL_w, 
#      MH_w, 
#      ML_w, 
#      NH_w, 
#      NL_w, 
#      file = fname)
```


```{r}
S_sig_w <- S_w$w_adjusted[S_w$w_adjusted > c]
T_sig_w <- T_w$w_adjusted[T_w$w_adjusted > c]
M_sig_w <- M_w$w_adjusted[M_w$w_adjusted > c]
N_sig_w <- N_w$w_adjusted[N_w$w_adjusted > c]
L_sig_w <- L_w$w_adjusted[L_w$w_adjusted > c]
H_sig_w <- H_w$w_adjusted[H_w$w_adjusted > c]

df_sig_w <- data.frame(cond = rep('same', length(S_sig_w)), ws = S_sig_w) %>%
  rbind(data.frame(cond = rep('different', length(T_sig_w)), ws = T_sig_w)) %>%
  rbind(data.frame(cond = rep('meaningful', length(M_sig_w)), ws = M_sig_w)) %>%
  rbind(data.frame(cond = rep('nonsense', length(N_sig_w)), ws = N_sig_w)) %>%
  rbind(data.frame(cond = rep('low', length(L_sig_w)), ws = L_sig_w)) %>%
  rbind(data.frame(cond = rep('high', length(H_sig_w)), ws = H_sig_w))
df_sig_w$cond <- factor(df_sig_w$cond , levels=c("same", "different", "meaningful", "nonsense", "low", "high"))

# fit <- aov(ws ~ cond, data = df)
# summary(fit)
# TukeyHSD(fit)
# 
# # Plot
# df_talker_ws <- data.frame(cond = rep('same', length(SH_sig_w)), constraint = rep('high', length(SH_sig_w)), ws = SH_sig_w) %>%
#   rbind(data.frame(cond = rep('different', length(TH_sig_w)), constraint = rep('high', length(TH_sig_w)), ws = TH_sig_w)) %>%
#   rbind(data.frame(cond = rep('same', length(SL_sig_w)), constraint = rep('low', length(SL_sig_w)), ws = SL_sig_w)) %>%
#   rbind(data.frame(cond = rep('different', length(TL_sig_w)), constraint = rep('low', length(TL_sig_w)), ws = TL_sig_w))
# 
# fit <- aov(ws ~ constraint, data = df_talker_ws)
# summary(fit)
# TukeyHSD(fit)

ggplot(df_sig_w, aes(x = cond, y = ws)) +
  scale_fill_brewer(palette="Blues") +
  geom_signif(comparisons = list(c("different" , "same")), map_signif_level = TRUE) +
  geom_boxplot() +
  ylim(22, 35)
```

```{r}
talker_sig_w <- data.frame(cond = rep('Same', length(S_sig_w)), ws = S_sig_w) %>%
  rbind(data.frame(cond = rep('Different', length(T_sig_w)), ws = T_sig_w))
meaning_sig_w <- data.frame(cond = rep('Meaningful', length(M_sig_w)), ws = M_sig_w) %>%
  rbind(data.frame(cond = rep('Nonsense', length(N_sig_w)), ws = N_sig_w))
constraint_sig_w <- data.frame(cond = rep('Low', length(L_sig_w)), ws = L_sig_w) %>%
  rbind(data.frame(cond = rep('High', length(H_sig_w)), ws = H_sig_w))
# df_sig_w$cond <- factor(df_sig_w$cond , levels=c("same", "different", "meaningful", "nonsense", "low", "high"))

p_constraint <- ggplot(talker_sig_w, aes(x = cond, y = ws)) + 
  geom_boxplot() +
  geom_boxplot(fill = "#026fa1") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") +
  ylim(c(22, 35)) +
  ylab("w") +
  xlab('Talker') + 
  geom_signif(comparisons = list(c("Different", "Same")),  map_signif_level = TRUE)
p_meaning <- ggplot(meaning_sig_w, aes(x = cond, y = ws)) + 
  geom_boxplot() +
  geom_boxplot(fill = "#048fcf") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") + 
  ylim(c(22, 35)) +
  ylab("w") +
  xlab('Meaning')
p_talker <- ggplot(constraint_sig_w, aes(x = cond, y = ws)) + 
  geom_boxplot() +
  geom_boxplot(fill = "#09a6ed") +
  theme(legend.position = "none") +
  ylim(c(22, 35)) +
  ylab("w") +
  xlab('Constraint')
p <- ggarrange(p_talker, p_meaning, p_constraint, ncol = 3, widths = c(2, 1.8, 1.8))
p
# ggsave(p, filename = '4_test_cross_correlations/figs/compare_condition_ws.png', width = 8, height = 4)
```

