---
title: "Average"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_knit$set(root.dir = "/Users/letitiaho/src/talker_change_data_processing/")
setwd("/Users/letitiaho/src/talker_change_data_processing/")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("kableExtra")
source("tools/functions.R")
source("4_test_cross_correlations/src/functions.R")
```

```{r}
# Import data
xcorr <- read.csv(file = "3_cross_correlate/data/maximum.csv")
channels <- as.character(1:128)
```

```{r}
# Split into conditionns
#   Same-talker = S
#   Different-talker = T
#   Meaningful = M
#   Nonsense = N
#   Low constraint = L
#   High constraint = H
S <- subset(xcorr, talker = "S") %>% get_subject_averages()
T <- subset(xcorr, talker = "T") %>% get_subject_averages()
M <- subset(xcorr, meaning = "M") %>% get_subject_averages()
N <- subset(xcorr, meaning = "N") %>% get_subject_averages()
L <- subset(xcorr, constraint = "L") %>% get_subject_averages()
H <- subset(xcorr, constraint = "H") %>% get_subject_averages()
```

```{r}
# Function for making color coded table for p-values
p_table <- function(dat) {
  color_ps <- mutate_if(dat, is.numeric, function(x) {round(x, digits = 3)}) %>%
    mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                              cell_spec(x, NULL),
                                              cell_spec(x, background = spec_color(x, 
                                                                                   direction = 1, 
                                                                                   begin = 0.65, 
                                                                                   end = 1, 
                                                                                   option = "B", 
                                                                                   scale_from = c(0,0.1))))})
  
  kable(color_ps, escape = F, col.names = c("Channel", "S", "T", "M", "N", "S", "G")) %>%
    add_header_above(c(" " = 1, "Talker" = 2, "Meaning" = 2, "Constraint" = 2)) %>%
    kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
  # return(map_df)
}
```


### Create baseline

```{r}
overall <- get_subject_averages(xcorr)
baseline <- apply(overall, 2, mean) %>%
  rep(11) %>%
  matrix(nrow = 11, byrow = TRUE) # Cast it so baseline is the same shape as the condition cross correlation matrices
```

## One-sample wilcoxon for each baselined condition, against mu = 0

Compares the cross correlations for each condition level (e.g. same-talker, meaningful) to 0.

```{r}
S_baselined <- S-baseline
T_baselined <- T-baseline
M_baselined <- M-baseline
N_baselined <- N-baseline
L_baselined <- L-baseline
H_baselined <- H-baseline
```

```{r}
get_one_sample_wilcoxon_for_each_channel <- function(data, alt, MU = 0) {
  w <- apply(data, MARGIN = 2, function(channel) {wilcox.test(channel, 
                                                              exact = TRUE,
                                                              mu = MU,
                                                              alternative = c(alt))$statistic})
  p <- apply(data, MARGIN = 2, function(channel) {wilcox.test(channel, 
                                                              exact = TRUE, 
                                                              mu = MU,
                                                              alternative = c(alt))$p.value})
  return(data.frame("w" = w, "p" = p))
}
```

#### Greater than

```{r}
# Compare to 0
S_w_greater <- get_one_sample_wilcoxon_for_each_channel(S_baselined, alt = 'greater')
T_w_greater <- get_one_sample_wilcoxon_for_each_channel(T_baselined, alt = 'greater')
M_w_greater <- get_one_sample_wilcoxon_for_each_channel(M_baselined, alt = 'greater')
N_w_greater <- get_one_sample_wilcoxon_for_each_channel(N_baselined, alt = 'greater')
L_w_greater <- get_one_sample_wilcoxon_for_each_channel(L_baselined, alt = 'greater')
H_w_greater <- get_one_sample_wilcoxon_for_each_channel(H_baselined, alt = 'greater')
```

```{r}
# Creating a table to display all the p-values
greater_w <- data.frame(channels, 
                     'S' = S_w_greater$p,
                     'T' = T_w_greater$p, 
                     'M' = M_w_greater$p,
                     'N' = N_w_greater$p, 
                     'L' = L_w_greater$p,
                     'H' = H_w_greater$p)
p_table(greater_w)
```

#### Lesser than

```{r}
S_w_less <- get_one_sample_wilcoxon_for_each_channel(S_baselined, alt = 'less')
T_w_less <- get_one_sample_wilcoxon_for_each_channel(T_baselined, alt = 'less')
M_w_less <- get_one_sample_wilcoxon_for_each_channel(M_baselined, alt = 'less')
N_w_less <- get_one_sample_wilcoxon_for_each_channel(N_baselined, alt = 'less')
L_w_less <- get_one_sample_wilcoxon_for_each_channel(L_baselined, alt = 'less')
H_w_less <- get_one_sample_wilcoxon_for_each_channel(H_baselined, alt = 'less')
```

```{r}
# Creating a table to display all the p-values
less_w <- data.frame(channels, 
                     'S' = S_w_less$p,
                     'T' = T_w_less$p, 
                     'M' = M_w_less$p,
                     'N' = N_w_less$p, 
                     'L' = L_w_less$p,
                     'H' = H_w_less$p)
p_table(less_w)
```

## One-sample Wilcoxon against baseline mu, better approach

Instead of baselining the cross correlation values by subtracting the baseline value from them, simply compute a two-sample wilcoxon against mu = baseline.

```{r}
mu <- apply(overall, 2, mean)
```

```{r}
get_one_sample_wilcoxon_for_each_channel_against_mu <- function(data, mu, alt) {
  w <- mapply(function(x, y, z) {t.test(x, exact = TRUE, mu = y, alt = z)$statistic}, data, mu, alt)
  p <- mapply(function(x, y, z) {t.test(x, exact = TRUE, mu = y, alt = z)$p.value}, data, mu, alt)
  return(data.frame("w" = w, "p" = p))
}
```

#### Greater than

```{r}
S_w_mu_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(S, mu = mu, alt = 'greater')
T_w_mu_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(T, mu = mu, alt = 'greater')
M_w_mu_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(M, mu = mu, alt = 'greater')
N_w_mu_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(N, mu = mu, alt = 'greater')
L_w_mu_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(L, mu = mu, alt = 'greater')
H_w_mu_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(H, mu = mu, alt = 'greater')
```

```{r}
# Creating a table to display all the p-values
two_sample_greater <- data.frame(channels, 
                     'S' = S_w_mu_greater$p,
                     'T' = T_w_mu_greater$p, 
                     'M' = M_w_mu_greater$p,
                     'N' = N_w_mu_greater$p, 
                     'L' = L_w_mu_greater$p,
                     'H' = H_w_mu_greater$p)
p_table(two_sample_greater)
```

#### Less than

```{r}
S_w_mu_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(S, mu = mu, alt = 'less')
T_w_mu_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(T, mu = mu, alt = 'less')
M_w_mu_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(M, mu = mu, alt = 'less')
N_w_mu_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(N, mu = mu, alt = 'less')
L_w_mu_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(L, mu = mu, alt = 'less')
H_w_mu_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(H, mu = mu, alt = 'less')
```

```{r}
# Creating a table to display all the p-values
two_sample_less <- data.frame(channels, 
                     'S' = S_w_mu_less$p,
                     'T' = T_w_mu_less$p, 
                     'M' = M_w_mu_less$p,
                     'N' = N_w_mu_less$p, 
                     'L' = L_w_mu_less$p,
                     'H' = H_w_mu_less$p)
p_table(two_sample_less)
```


## Two Sample Wilcoxon comparing conditions

```{r}
# Functions
get_two_sample_wilcoxon_for_each_channel <- function(group1, group2, paired = TRUE) {
  w <- mapply(function(x, y, z) {wilcox.test(x, y, paired = z, exact = TRUE)$statistic}, group1, group2, paired)
  p <- mapply(function(x, y, z) {wilcox.test(x, y, paired = z, exact = TRUE)$p.value}, group1, group2, paired)
  return(data.frame("w" = w, "p" = p))
}

p_table_two_sample <- function(dat) {
  map_df <-  mutate_if(dat, is.numeric, function(x) {round(x, digits = 3)}) %>%
    mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                              cell_spec(x, NULL),
                                              cell_spec(x, background = spec_color(x, 
                                                                                   direction = 1, 
                                                                                   begin = 0.65, 
                                                                                   end = 1, 
                                                                                   option = "B", 
                                                                                   scale_from = c(0,0.1))))})
  
  kable(map_df, escape = F, col.names = c("Channel", "Talker", "Meaning", "Constraint")) %>%
    kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
}
```

```{r}
talker_w <- get_two_sample_wilcoxon_for_each_channel(S, T)
meaning_w <- get_two_sample_wilcoxon_for_each_channel(M, N)
constraint_w <- get_two_sample_wilcoxon_for_each_channel(L, H)
```

```{r}
two_sample_w <- data.frame(channels, 
                     'talker' = talker_w$p,
                     'meaning' = meaning_w$p,
                     'constraint' = constraint_w$p)
p_table_two_sample(two_sample_w)
```

## Interactions

```{r}
p_table_interaction <- function(dat) {
map_df <- mutate_if(dat, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "L", "H", "L", "H", "L", "H", "L", "H")) %>%
  add_header_above(c(" " = 1, "Same-talker" = 2, "Different-talker" = 2, "Meaningful" = 2, "Nonsense" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
}
```

```{r}
# Subset talker
SL <- subset(xcorr, talker = "S", constraint = "L") %>% get_subject_averages()
SH <- subset(xcorr, talker = "S", constraint = "H") %>% get_subject_averages()
TL <- subset(xcorr, talker = "T", constraint = "L") %>% get_subject_averages()
TH <- subset(xcorr, talker = "T", constraint = "H") %>% get_subject_averages()

# Subset meaning
ML <- subset(xcorr, meaning = "M", constraint = "L") %>% get_subject_averages()
MH <- subset(xcorr, meaning = "M", constraint = "H") %>% get_subject_averages()
NL <- subset(xcorr, meaning = "N", constraint = "L") %>% get_subject_averages()
NH <- subset(xcorr, meaning = "N", constraint = "H") %>% get_subject_averages()
```

#### Greater than

```{r}
# One-sample t-tests for talker
SL_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(SL, mu = mu, alt = 'greater')
SH_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(SH, mu = mu, alt = 'greater')
TL_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(TL, mu = mu, alt = 'greater')
TH_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(TH, mu = mu, alt = 'greater')

# One-sample t-tests for meaning
ML_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(ML, mu = mu, alt = 'greater')
MH_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(MH, mu = mu, alt = 'greater')
NL_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(NL, mu = mu, alt = 'greater')
NH_w_greater <- get_one_sample_wilcoxon_for_each_channel_against_mu(NH, mu = mu, alt = 'greater')
```

```{r}
# Creating a table to display all the p-values
interaction_w_greater <- data.frame(channels, 
                     'SL' = SL_w_greater$p,
                     'SH' = SH_w_greater$p,
                     'TL' = TL_w_greater$p,
                     'TH' = TH_w_greater$p, 
                     'ML' = ML_w_greater$p,
                     'MH' = MH_w_greater$p,
                     'NL' = NL_w_greater$p,
                     'NH' = NH_w_greater$p)
p_table_interaction(interaction_w_greater)
```

#### Less than

```{r}
# One-sample t-tests for talker
SL_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(SL, mu = mu, alt = 'less')
SH_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(SH, mu = mu, alt = 'less')
TL_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(TL, mu = mu, alt = 'less')
TH_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(TH, mu = mu, alt = 'less')

# One-sample t-tests for meaning
ML_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(ML, mu = mu, alt = 'less')
MH_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(MH, mu = mu, alt = 'less')
NL_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(NL, mu = mu, alt = 'less')
NH_w_less <- get_one_sample_wilcoxon_for_each_channel_against_mu(NH, mu = mu, alt = 'less')
```

```{r}
# Creating a table to display all the p-values
interaction_w_less <- data.frame(channels, 
                     'SL' = SL_w_less$p,
                     'SH' = SH_w_less$p,
                     'TL' = TL_w_less$p,
                     'TH' = TH_w_less$p, 
                     'ML' = ML_w_less$p,
                     'MH' = MH_w_less$p,
                     'NL' = NL_w_less$p,
                     'NH' = NH_w_less$p)
p_table_interaction(interaction_w_less)
```


## Save variables for mapping

```{r}
save(S_w_mu_greater, T_w_mu_greater, M_w_mu_greater, N_w_mu_greater, talker_w, meaning_w, constraint_w, file = "4_test_cross_correlations/data/wilcoxon_against_overall.RData")
```

