---
title: "Average"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_knit$set(root.dir = "/Users/letitiaho/src/talker_change_data_processing/")
setwd("/Users/letitiaho/src/talker_change_data_processing/")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("kableExtra")
library("tidyr")
source("tools/functions.R")
source("4_test_cross_correlations/src/functions.R")
```

```{r}
band = "above_f0"

# Import data
xcorr <- read.csv(file = paste("3_cross_correlate/data/average_", band, "_normalized.csv", sep = ''))
channels <- as.character(1:128)
subs <- as.character(unique(xcorr$subject_number))
n <- length(subs)
conds <- unique(c(xcorr$constraint, xcorr$meaning, xcorr$talker))
```

#### One-sample t-tests for overall tracking

```{r}
overall <- get_subject_averages(xcorr)
overall_w <- get_one_sample_wilcoxon_for_each_channel(overall)
spacer <- matrix(" ", 128, 1)
overall_ps <- data.frame(channels, 'p'= overall_w$p)
```


#### One-sample wilcoxon for each condition

Compares the cross correlations for each condition level (e.g. same-talker, meaningful) to 0.

```{r}
S <- subset(xcorr, talker = "S") %>% get_subject_averages()
T <- subset(xcorr, talker = "T") %>% get_subject_averages()
M <- subset(xcorr, meaning = "M") %>% get_subject_averages()
N <- subset(xcorr, meaning = "N") %>% get_subject_averages()
L <- subset(xcorr, constraint = "L") %>% get_subject_averages()
H <- subset(xcorr, constraint = "H") %>% get_subject_averages()
```

```{r}
S_w <- get_one_sample_wilcoxon_for_each_channel(S)
T_w <- get_one_sample_wilcoxon_for_each_channel(T)
M_w <- get_one_sample_wilcoxon_for_each_channel(M)
N_w <- get_one_sample_wilcoxon_for_each_channel(N)
L_w <- get_one_sample_wilcoxon_for_each_channel(L)
H_w <- get_one_sample_wilcoxon_for_each_channel(H)
```

**Get some stats**

```{r}
sum(overall_w$p < 0.05)
sum(T_w$p < 0.05)
sum(S_w$p < 0.05)
sum(M_w$p < 0.05)
sum(N_w$p < 0.05)
sum(L_w$p < 0.05)
sum(H_w$p < 0.05)
```

#### Two-sample Wilcoxon

Compares cross correlations between the two levels of each condition. 

```{r}
standardize_ws <- function(p, w) {
  i <- which(p == max(p))
  mid <- w[i]
  w_adjusted <- abs(w - mid)
  return(w_adjusted)
}

get_critical_value <- function(p, w) {
  c <- min(w[which(p < 0.05)])
  return(c)
}

plot_ws <- function(w1, w2, labs, c, fname) {
  df_long <- data.frame(w1 = unlist(w1), w2 = unlist(w2)) %>%
    pivot_longer(cols = c("w1", "w2"),
                 names_to = "condition",
                 values_to = "W")
  p <- ggplot(df_long, aes(x = W, fill = condition)) +
    geom_histogram(position ="identity", alpha=0.65, bins = 15) +
    geom_vline(xintercept = c) +
    scale_fill_discrete(labels = labs) +
    scale_color_discrete(labels = labs) +
    ylim(c(0, 25)) +
    xlim(c(0, 35))
  # ggsave(p, filename = fname, width = 12, height = 7)
  return(p)
}

talker_w <- get_two_sample_wilcoxon_for_each_channel(S, T, paired = TRUE)
meaning_w <- get_two_sample_wilcoxon_for_each_channel(M, N, paired = TRUE)
constraint_w <- get_two_sample_wilcoxon_for_each_channel(L, H, paired = TRUE)

talker_w$w_adjusted <-standardize_ws(talker_w$p, talker_w$w)
meaning_w$w_adjusted <-standardize_ws(meaning_w$p, meaning_w$w)
constraint_w$w_adjusted <-standardize_ws(constraint_w$p, constraint_w$w)
```

**Get some stats**

```{r}
sum(talker_w$p < 0.05)
sum(meaning_w$p < 0.05)
sum(constraint_w$p < 0.05)
```

#### Plot test statistics for each condition

```{r}
# Plot p-values
hist(S_w$p, ylim = c(0,40))
hist(T_w$p, ylim = c(0,40))
hist(M_w$p, ylim = c(0,40))
hist(N_w$p, ylim = c(0,40))
hist(L_w$p, ylim = c(0,40))
hist(H_w$p, ylim = c(0,40))
```

```{r}
# Plot test statistics
overall_w$w_adjusted <- standardize_ws(overall_w$p, overall_w$w)
S_w$w_adjusted <- standardize_ws(S_w$p, S_w$w)
T_w$w_adjusted <- standardize_ws(T_w$p, T_w$w)
M_w$w_adjusted <- standardize_ws(M_w$p, M_w$w)
N_w$w_adjusted <- standardize_ws(N_w$p, N_w$w)
L_w$w_adjusted <- standardize_ws(L_w$p, L_w$w)
H_w$w_adjusted <- standardize_ws(H_w$p, H_w$w)

c <- get_critical_value(S_w$p, S_w$w_adjusted)

plot_ws(T_w$w_adjusted, S_w$w_adjusted, c("T", "S"), c, "4_test_cross_correlations/figs/ws_talker_poster.png")
plot_ws(N_w$w_adjusted, M_w$w_adjusted, c("N", "M"), c, "4_test_cross_correlations/figs/ws_meaning_poster.png")
plot_ws(H_w$w_adjusted, L_w$w_adjusted, c("H", "L"), c, "4_test_cross_correlations/figs/ws_constraint_poster.png")
```

```{r}
p <- ggplot(overall_w, aes(x = w_adjusted)) +
    geom_histogram(position ="identity", alpha=0.8, bins = 15) +
    geom_vline(xintercept = c) +
    scale_fill_discrete(labels = labs) +
    scale_color_discrete(labels = labs) +
    ylim(c(0, 25)) +
    xlim(c(0, 35)) +
    xlab("w")
p 
ggsave(filename = paste("4_test_cross_correlations/figs/ws_overall_", band, ".png", sep = ''), plot = p, width = 6, height = 2.5)
sum(overall_w$p < 0.05)
```


#### Plot cross correlations

```{r}
# Plot cross correlations for channels with significant cross correlations

get_sig_xcorrs <- function(xcorr, p) { # get xcorrs from sig channels
  sig_xcorr <- as.matrix(xcorr) %>%
   .[, which(p < 0.05)] %>%
    abs()
  print(dim(sig_xcorr))

  # Catch cases in which there is only one significant channels
  if (class(sig_xcorr) == 'numeric') {
    print("Only one significant channel")
    return(sig_xcorr)
  }
  
  # Catch cases in which there are no significant channels
  if (dim(sig_xcorr)[2] == 0) {
    print("No significant channels")
    return(0)
  }

  sig_xcorr <- rowMeans(sig_xcorr) %>% # colMeans() compares channels, rowMeans() compares subs
    remove_outliers()
  return(sig_xcorr)
}

get_sig_xcorrs_df <- function(condition, group, sig_xcorr) {
  condition_col <- rep(condition, length(sig_xcorr))
  group_col <- rep(group, length(sig_xcorr))
  df <- data.frame(condition, sig_xcorr, group)
}

remove_outliers <- function(x) {
  x <- x[!x %in% boxplot.stats(x)$out]
  return(x)
}

S_sig <- get_sig_xcorrs(S, S_w$p)
T_sig <- get_sig_xcorrs(T, T_w$p)
M_sig <- get_sig_xcorrs(M, M_w$p)
N_sig <- get_sig_xcorrs(N, N_w$p)
L_sig <- get_sig_xcorrs(L, L_w$p)
H_sig <- get_sig_xcorrs(H, H_w$p)
```

```{r}
df_talker <- get_sig_xcorrs_df('S', 'talker', S_sig) %>%
  rbind(get_sig_xcorrs_df('T', 'talker', T_sig))
df_meaning <- rbind(get_sig_xcorrs_df('M', 'meaning', M_sig)) %>%
  rbind(get_sig_xcorrs_df('N', 'meaning', N_sig))
df_constraint <- rbind(get_sig_xcorrs_df('L', 'constraint', L_sig)) %>%
  rbind(get_sig_xcorrs_df('H', 'constraint', H_sig))

# New facet label names for condition variable
# condition.labs <- c("S", "T", "M", "N", "L", "H")

p_talker <- ggplot(df_talker, aes(x = condition, y = sig_xcorr, fill = group)) +
  geom_boxplot(fill = "#09a6ed") +
  geom_signif(comparisons = list(c("S", "T")), map_signif_level = TRUE) +
  ylab("cross correlations") +
  ylim(c(0, 1e-05)) +
  theme(legend.position = "none") +
  xlab('Talker')
p_meaning <- ggplot(df_meaning, aes(x = condition, y = sig_xcorr, fill = group)) +
  geom_boxplot(fill = "#048fcf") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") +
  ylim(c(0, 1e-05)) +
  xlab('Meaning')
p_constraint <- ggplot(df_constraint, aes(x = condition, y = sig_xcorr, fill = group)) +
  geom_boxplot(fill = "#026fa1") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y =element_blank(),
        legend.position = "none") +
  ylim(c(0, 1e-05)) +
  xlab('Constraint')
p <- ggarrange(p_talker, p_meaning, p_constraint, ncol = 3)
p

ggsave(p, filename = paste("4_test_cross_correlations/figs/xcorrs_for_sig_channels_", band, ".png", sep = ''), width = 10, height = 5)
```



#### Get stats

```{r}
# one-sample t-test
overall_sig <- get_sig_xcorrs(overall, overall_w$p)
t.test(overall_sig)

# t-tests between levels 
t.test(T_sig, S_sig)
t.test(M_sig, N_sig)
t.test(H_sig, L_sig)
```

#### Save everything

```{r}
save(overall_w,
     S_w,
     T_w,
     M_w,
     N_w,
     L_w,
     H_w,
     talker_w,
     meaning_w,
     constraint_w,
     file = paste('4_test_cross_correlations/data/wilcoxon_results_', band, '.RData', sep = '')
)
```
