---
title: "Average"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_knit$set(root.dir = "/Users/letitiaho/src/talker_change_data_processing/")
setwd("/Users/letitiaho/src/talker_change_data_processing/")
library("dplyr")
library("ggplot2")
library("ggpubr")
library("kableExtra")
source("tools/functions.R")
source("8_tests/src/functions.R")
```

```{r}
# Import data
xcorr <- read.csv(file = "2_cross_correlate/data/average.csv")
channels <- as.character(1:128)
```

#### One-sample t-tests for overall tracking

```{r}
channel_labels <- paste("X", as.character(1:128), sep = "")
all_channels <- select(xcorr, all_of(channel_labels))
w <- get_one_sample_wilcoxon(all_channels)

# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
overall <- data.frame(channels, w$p)
map_df <- mutate_if(overall, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1,
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x,
                                                                                 direction = 1,
                                                                                 begin = 0.65,
                                                                                 end = 1,
                                                                                 option = "B",
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "p")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```



#### One-sample wilcoxon for each condition

Compares the cross correlations for each condition level (e.g. same-talker, meaningful) to 0.

```{r}
# Data frames will be named according to their condition, with the code for talker, then meaning, then constraint listed in that order
# Same-talker = S
# Different-talker = T
# Meaningful = M
# Nonsense = N
# Low constraint = L
# High constraint = H
S <- subset(xcorr, talker = "S")
T <- subset(xcorr, talker = "T")
M <- subset(xcorr, meaning = "M")
N <- subset(xcorr, meaning = "N")
L <- subset(xcorr, constraint = "L")
H <- subset(xcorr, constraint = "H")
```

```{r}
S_w <- get_one_sample_wilcoxon(S)
T_w <- get_one_sample_wilcoxon(T)
M_w <- get_one_sample_wilcoxon(M)
N_w <- get_one_sample_wilcoxon(N)
L_w <- get_one_sample_wilcoxon(L)
H_w <- get_one_sample_wilcoxon(H)
```

```{r}
# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
one_sample_w <- data.frame(channels, 
                     S_w$p,
                     T_w$p, 
                     spacer,
                     M_w$p,
                     N_w$p, 
                     spacer,
                     L_w$p,
                     H_w$p)
map_df <- mutate_if(one_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "S", "T", " ", "M", "N", " ", "S", "G")) %>%
  add_header_above(c(" " = 1, "Talker" = 2, " "  = 1, "Meaning" = 2, " " = 1, "Constraint" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

#### Two-sample Wilcoxon

Compares cross correlations between the two levels of each condition. 

```{r}
talker_w <- get_two_sample_wilcoxon(S, T)
meaning_w <- get_two_sample_wilcoxon(M, N)
constraint_w <- get_two_sample_wilcoxon(L, H)
```

```{r}
# Creating a table to display all the p-values
two_sample_w <- data.frame(channels, 
                     talker_w$p,
                     meaning_w$p,
                     constraint_w$p)
map_df <-  mutate_if(two_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "Talker", "Meaning", "Constraint")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

#### Wilcoxon with interaction by constraint

```{r}
# Subset talker
SL <- subset(xcorr, talker = "S", constraint = "L")
SH <- subset(xcorr, talker = "S", constraint = "H")
TL <- subset(xcorr, talker = "T", constraint = "L")
TH <- subset(xcorr, talker = "T", constraint = "H")

# Subset meaning
ML <- subset(xcorr, meaning = "M", constraint = "L")
MH <- subset(xcorr, meaning = "M", constraint = "H")
NL <- subset(xcorr, meaning = "N", constraint = "L")
NH <- subset(xcorr, meaning = "N", constraint = "H")
```

```{r}
# One-sample t-tests for talker
SL_w <- get_one_sample_wilcoxon(SL)
SH_w <- get_one_sample_wilcoxon(SH)
TL_w <- get_one_sample_wilcoxon(TL)
TH_w <- get_one_sample_wilcoxon(TH)

# One-sample t-tests for meaning
ML_w <- get_one_sample_wilcoxon(ML)
MH_w <- get_one_sample_wilcoxon(MH)
NL_w <- get_one_sample_wilcoxon(NL)
NH_w <- get_one_sample_wilcoxon(NH)
```

```{r}
# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
interaction_w <- data.frame(channels, 
                     SL_w$p,
                     SH_w$p,
                     spacer,
                     TL_w$p,
                     TH_w$p, 
                     spacer,
                     ML_w$p,
                     MH_w$p,
                     spacer,
                     NL_w$p,
                     NH_w$p)
map_df <- mutate_if(interaction_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "L", "H", " ", "L", "H", " ", "L", "H", " ", "L", "H")) %>%
  add_header_above(c(" " = 1, "Same-talker" = 2, " "  = 1, "Different-talker" = 2, " " = 1, "Meaningful" = 2, " "  = 1, "Nonsense" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
talker_L_w <- get_two_sample_wilcoxon(SL, TL)
talker_H_w <- get_two_sample_wilcoxon(SH, TH)
meaning_L_w <- get_two_sample_wilcoxon(ML, NL)
meaning_H_w <- get_two_sample_wilcoxon(MH, NH)
```

```{r}
# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
interaction_two_sample_w <- data.frame(channels, 
                     talker_L_w$p,
                     talker_H_w$p,
                     spacer,
                     meaning_L_w$p,
                     meaning_H_w$p)
map_df <- mutate_if(interaction_two_sample_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "L", "H", " ", "L", "H")) %>%
  add_header_above(c(" " = 1, "Talker" = 2, " "  = 1, "Meaning" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

#### T-tests against difference set by low vs high-constraint sentences

```{r}
SML <- subset(xcorr, talker = "S", meaning = "M", constraint = "L", keep_subject_numbers = T)
SML_means <- aggregate(SML[,2:129], by=list(SML$subject_number), FUN=mean) %>%
  subset(-1)
```

```{r}
# take meaningful and same-talker sentences and compare correlations of low- vs high-constraint sentences
# compare this difference to meaningful and high-constraint same- vs different-talker sentences
# compare this difference to same-talker and high-constraint meaningful vs nonsense sentences
SML <- subset(xcorr, talker = "S", meaning = "M", constraint = "L", keep_subject_numbers = T)
SML_means <- aggregate(SML[,2:129], by=list(SML$subject_number), FUN=mean) %>%
  subset(SML_means, -1)
SMH <- subset(xcorr, talker = "S", meaning = "M", constraint = "H", keep_subject_numbers = T)
SMH_means <- aggregate(SMH[,2:129], by=list(SMH$subject_number), FUN=mean) %>%
  subset(SML_means, -1)
baseline <- SMH_means - SML_means

TMH <- subset(xcorr, talker = "T", meaning = "M", constraint = "H", keep_subject_numbers = T)
TMH_means <- aggregate(TMH[,2:129], by=list(TMH$subject_number), FUN=mean) %>%
  subset(SML_means, -1)
talker_compare <- TMH_means - SMH_means

SNH <- subset(xcorr, talker = "S", meaning = "N", constraint = "H", keep_subject_numbers = T)
SNH_means <- aggregate(SNH[,2:129], by=list(SNH$subject_number), FUN=mean) %>%
  subset(SML_means, -1)
meaning_compare <- SNH_means - SMH_means
```

```{r}
# t-test by subject
talker_compare_w <- get_two_sample_wilcoxon(baseline, talker_compare)
meaning_compare_w <- get_two_sample_wilcoxon(baseline, meaning_compare)
```

```{r}
# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
compare_w <- data.frame(channels, 
                     talker_compare_w$p,
                     meaning_compare_w$p)
map_df <- mutate_if(compare_w, is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

kable(map_df, escape = F, col.names = c("Channel", "Talker", "Meaning")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
save(overall, one_sample_w, two_sample_w, interaction_w, interaction_two_sample_w, compare_w, file = "8_tests/data/wilcoxon_results.RData")
```

