---
title: "Talker change data processing"
author: "Letitia Ho"
date: "8/12/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
require("knitr")
library("dplyr")
library("kableExtra")
```

``` {r load_data, echo=FALSE, warning=FALSE}
setwd('/Applications/eeglab2019/talker-change-data-processing/')
xcorr <- read.csv('data/aggregate/cross_correlation_data.csv')
conv <- read.csv('data/aggregate/convolution_data.csv')
# xcorr_formants <- read.csv('data/aggregate/cross_correlation_formant_data.csv')
# conv_formants <- read.csv('data/aggregate/convolution_formant_data.csv')
```

```{r get_one_sample_t, message=FALSE, include=FALSE}
get_one_sample_t <- function(data) {
  channel_columns = paste("X", 1:128, sep = "")
  channels <- select(data, all_of(channel_columns))
  t <- apply(channels, MARGIN = 2, function(channel) {t.test(channel)$statistic})
  df <- apply(channels, MARGIN = 2, function(channel) {t.test(channel)$parameter})
  p <- apply(channels, MARGIN = 2, function(channel) {t.test(channel)$p.value})
  return(data.frame("t" = t, "df" = df, "p" = p))
}
```

```{r get_paired_samples_t, message=FALSE, include=FALSE}
get_paired_samples_t <- function(group1, group2) {
  channel_columns = paste("X", 1:128, sep = "")
  group1 <- select(group1, all_of(channel_columns))
  group2 <- select(group2, all_of(channel_columns))
  t <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$statistic}, group1, group2)
  df <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$parameter}, group1, group2)
  p <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$p.value}, group1, group2)
  return(data.frame("t" = t, "df" = df, "p" = p))
  }
```

```{r get_hot, message=FALSE, include=FALSE}
get_hot <- function(data) {
  hot <- c()
  hot[data$p < 0.1] <- 1
  hot[data$p > 0.1] <- 0
  return(hot)
}
```

```{r get_frequency_table, message=FALSE, include=FALSE}
get_frequency_table <- function(data) {
    hot <- get_hot(data)
    counts <- margin.table(table(hot), 1)
    proportions <- prop.table(table(hot))
    return(data.frame("counts" = c(counts[1], counts[2]), "proportion" = c(proportions[1], proportions[2])))
  }
```

```{r get_combined_frequency_table, message=FALSE, include=FALSE}
get_combined_frequency_table <- function(xcorr, conv, title = NULL) {
  xcorr_freqs <- get_frequency_table(xcorr)
  conv_freqs <- get_frequency_table(conv)
  kable(cbind(xcorr_freqs, conv_freqs), caption = title) %>%
    kable_styling(c("striped", "condensed"), full_width = F) %>%
    add_header_above(c(" ", "Cross-correlation" = 2, "Convolution" = 2))
}
```



******

#### 1. Do cortical regions track temporal variation in the speech signal?

``` {r, echo=FALSE}
xcorr_all_conditions <- get_one_sample_t(xcorr)
conv_all_conditions <- get_one_sample_t(conv)
get_combined_frequency_table(xcorr_all_conditions, conv_all_conditions, title = "Table 1. Channels significantly tracking the stimuli")
```

**Output 1. Channels with significant cross-correlation with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the cross-correlation of each stimulus waveform with each electrode EEG trace across all conditions.

```{r, echo=FALSE}
xcorr_all_conditions[which(xcorr_all_conditions$p < 0.1),]
```

**Output 2. Channels with significant convolution with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the convolution of each stimulus waveform with each electrode EEG trace across all conditions.

```{r, echo=FALSE}
conv_all_conditions[which(conv_all_conditions$p < 0.1),]
```

************

#### 2. Do cortical regions track differently depending on the conditions?

Tested by one-sample t-tests for significant waveform tracking in each level of each condition.

**Channels significantly tracking the stimuli in the talker condition** 

```{r, echo=FALSE}
xcorr_talker_s <- get_one_sample_t(filter(xcorr, talker == 'S'))
conv_talker_s <- get_one_sample_t(filter(conv, talker == 'S'))
get_combined_frequency_table(xcorr_talker_s, conv_talker_s, title = "Table 2. Same talker")
xcorr_talker_t <- get_one_sample_t(filter(xcorr, talker == 'T'))
conv_talker_t <- get_one_sample_t(filter(conv, talker == 'T'))
get_combined_frequency_table(xcorr_talker_t, conv_talker_t, title = "Table 3. Different talker")
```

**Channels significantly tracking the stimuli in the meaning condition** 

```{r, echo=FALSE}
xcorr_meaning_m <- get_one_sample_t(filter(xcorr, meaning == 'M'))
conv_meaning_m <- get_one_sample_t(filter(conv, meaning == 'M'))
get_combined_frequency_table(xcorr_meaning_m, conv_meaning_m, title = "Table 4. Meaningful")
xcorr_meaning_n <- get_one_sample_t(filter(xcorr, meaning == 'N'))
conv_meaning_n <- get_one_sample_t(filter(conv, meaning == 'N'))
get_combined_frequency_table(xcorr_meaning_n, conv_meaning_n, title = "Table 5. Nonsense")
```

**Channels significantly tracking the stimuli in the constraint condition** 

```{r, echo=FALSE}
xcorr_constraint_s <- get_one_sample_t(filter(xcorr, constraint == 'S'))
conv_constraint_s <- get_one_sample_t(filter(conv, constraint == 'S'))
get_combined_frequency_table(xcorr_constraint_s, conv_constraint_s, title = "Table 6. High constraint")
xcorr_constraint_g <- get_one_sample_t(filter(xcorr, constraint == 'G'))
conv_constraint_g <- get_one_sample_t(filter(conv, constraint == 'G'))
get_combined_frequency_table(xcorr_constraint_g, conv_constraint_g, title = "Table 7. Low constraint")
```

**Table 8. *p*-values for each level in each condition**

```{r, echo=FALSE}
level_p_values <- data.frame(substr(row.names(xcorr_talker_s), 2, 10), 
                     xcorr_talker_s$p, conv_talker_s$p, 
                     xcorr_talker_t$p, conv_talker_t$p,
                     xcorr_meaning_m$p, conv_meaning_m$p,
                     xcorr_meaning_n$p, conv_meaning_n$p,
                     xcorr_constraint_s$p, conv_constraint_s$p,
                     xcorr_constraint_g$p, conv_constraint_g$p)  %>%
  mutate_if(is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x < 0.1, cell_spec(x, bold = F, color = spec_color(x, direction = -1)),
    cell_spec(x, bold = F, color = "black"))})

kable(level_p_values, escape = F, col.names = c("Channel", "XCorr", "Conv", "XCorr", "Conv",
                                        "XCorr", "Conv", "XCorr", "Conv",
                                        "XCorr", "Conv", "XCorr", "Conv"))  %>%
  add_header_above(c(" " = 1, "Same talker" = 2, "Different talker" = 2,
                     "Meaningful" = 2, "Nonsense" = 2,
                     "High constraint" = 2, "Low constraint" = 2)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

************

#### 3. Do cortical regions track the levels of each condition differently?

Tested by paired-samples t-tests between the two levels of each condition. I.e. a test of whether an electrode significantly distinguishes condition levels.

**Channels significantly distinguishing the stimuli in each condition** 

```{r, echo=FALSE}
# Talker
xcorr_talker <- get_paired_samples_t(filter(xcorr, talker == 'S'), filter(xcorr, talker == 'T'))
conv_talker <- get_paired_samples_t(filter(conv, talker == 'S'), filter(conv, talker == 'T'))
get_combined_frequency_table(xcorr_talker, conv_talker, title = "Table 9. Talker")

# Meaning
xcorr_meaning <- get_paired_samples_t(filter(xcorr, meaning == 'M'), filter(xcorr, meaning == 'N'))
conv_meaning <- get_paired_samples_t(filter(conv, meaning == 'M'), filter(conv, meaning == 'N'))
get_combined_frequency_table(xcorr_meaning, conv_meaning, title = "Table 10. Meaning")

# Constraint
xcorr_constraint <- get_paired_samples_t(filter(xcorr, constraint == 'S'), filter(xcorr, constraint == 'G'))
conv_constraint <- get_paired_samples_t(filter(conv, constraint == 'S'), filter(conv, constraint == 'G'))
get_combined_frequency_table(xcorr_constraint, conv_constraint, title = "Table 11. Constraint")
```

**Table 12. *p*-values for each condition**

```{r, echo=FALSE}
# Match columns based on cross-correlation only

# talker_diff[which(xcorr_talker$p < 0.1)] <- 1
# talker_s_match
# talker_t_match
# talker_both_match
# 
# condition_p_values <- data.frame(substr(row.names(xcorr_talker_s), 2, 10), 
#                      xcorr_talker$p, conv_talker$p, 
#                      xcorr_meaning$p, conv_meaning$p,
#                      xcorr_constraint$p, conv_constraint$p) %>%
#   mutate_if(is.numeric, function(x) {round(x, digits = 3)}) %>%
#   mutate_if(is.numeric, function(x) {ifelse(x < 0.1, cell_spec(x, bold = F, color = spec_color(x, direction = -1)),
#     cell_spec(x, bold = F, color = "black"))})
# 
# kable(condition_p_values, escape = F, col.names = c("Channel", "XCorr", "Conv", "XCorr", "Conv", "XCorr", "Conv"))  %>%
#   add_header_above(c(" " = 1, "Talker" = 2, "Meaning" = 2, "Constraint" = 2)) %>%
#   kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

************

#### 4. Are the brain organizations different in different conditions related to tracking?

Tested by 

**Subheading** 


************

#### 5. What properties are being tracked in the meaning and talker conditions?

Tested by 

**Subheading** 