---
title: "Talker change data processing"
author: "Letitia Ho"
date: "8/12/2020"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
require("knitr")
library("dplyr")
opts_knit$set(root.dir = "/Applications/eeglab2019/talker-change-data-processing/")
```

``` {r load_data, echo=FALSE}
xcorr <- read.csv('data/aggregate/cross_correlation_data.csv')
conv <- read.csv('data/aggregate/convolution_data.csv')
# xcorr_formants <- read.csv('data/aggregate/cross_correlation_formant_data.csv')
# conv_formants <- read.csv('data/aggregate/convolution_formant_data.csv')
```


******

#### 1. Do cortical regions track temporal variation in the speech signal?

```{r, message=FALSE, include = FALSE}
one_sample_t <- function(data) {
  channel_columns = paste("X", 1:128, sep = "")
  channels <- select(data, channel_columns)
  p <- apply(channels, MARGIN = 2, function(channel) {t.test(channel)$p.value})
  t <- apply(channels, MARGIN = 2, function(channel) {t.test(channel)$statistic})
  df <- apply(channels, MARGIN = 2, function(channel) {t.test(channel)$parameter})
  return(data.frame("p" = p, "t" = t, "df" = df))
}

# Cross-correlation
xcorr_tracking <- one_sample_t(xcorr)
# Number of channels with significant tracking
xcorr_nchans <- sum(xcorr_tracking$p < 0.1)

# Convolution
conv_tracking <- one_sample_t(conv)
# Number of channels with significant tracking
conv_nchans <- sum(conv_tracking$p < 0.1)
```

**Table 1. Number of channels significantly tracking the stimuli**

| | count |
| --- | --- |
| cross correlation | `r xcorr_nchans` |
| convolution | `r conv_nchans` |

**Output 1. Channels with significant cross-correlation with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the cross-correlation of each stimulus waveform with each electrode EEG trace across all conditions.

```{r}
xcorr_tracking[which(xcorr_tracking$p < 0.1),]
```

**Output 2. Channels with significant convolution with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the convolution of each stimulus waveform with each electrode EEG trace across all conditions.

```{r}
conv_tracking[which(conv_tracking$p < 0.1),]
```

************

#### 2. Do cortical regions track differently depending on the conditions?

```{r}
one_sample_t_sig <- function(data) {
  channel_columns = paste("X", 1:128, sep = "")
  channels <- select(data, channel_columns)
  sig <- apply(channels, MARGIN = 2, function(channel) {t.test(channel)$p.value}) < 0.1
  return(sig)
}

```


```{r, message=FALSE, echo=FALSE}
# Cross-correlation
xcorr_same_talker <- one_sample_t_sig(filter(xcorr, talker == 'S'))
xcorr_same_talker
# xcorr_same_talker_nchans <- sum(xcorr_same_talker$p < 0.1)
# xcorr_diff_talker <- one_sample_t(filter(xcorr, talker == 'T'))
# xcorr_diff_talker_nchans <- sum(xcorr_diff_talker$p < 0.1)
# xcorr_meaningful <- one_sample_t(filter(xcorr, meaning == 'M'))
# xcorr_meaningful_nchans <- sum(xcorr_meaningful$p < 0.1)
# xcorr_nonsense <- one_sample_t(filter(xcorr, meaning == 'N'))
# xcorr_nonsense_nchans <- sum(xcorr_nonsense$p < 0.1)
# xcorr_general <- one_sample_t(filter(xcorr, constraint == 'G'))
# xcorr_general_nchans <- sum(xcorr_general$p < 0.1)
# xcorr_specific <- one_sample_t(filter(xcorr, constraint == 'S'))
# xcorr_specific_nchans <- sum(xcorr_specific$p < 0.1)
# 
# # Convolution
# conv_same_talker <- one_sample_t(filter(conv, talker == 'S'))
# conv_same_talker_nchans <- sum(conv_same_talker$p < 0.1)
# conv_diff_talker <- one_sample_t(filter(conv, talker == 'T'))
# conv_diff_talker_nchans <- sum(conv_diff_talker$p < 0.1)
# conv_meaningful <- one_sample_t(filter(conv, meaning == 'M'))
# conv_meaningful_nchans <- sum(conv_meaningful$p < 0.1)
# conv_nonsense <- one_sample_t(filter(conv, meaning == 'N'))
# conv_nonsense_nchans <- sum(conv_nonsense$p < 0.1)
# conv_general <- one_sample_t(filter(conv, constraint == 'G'))
# conv_general_nchans <- sum(conv_general$p < 0.1)
# conv_specific <- one_sample_t(filter(conv, constraint == 'S'))
# conv_specific_nchans <- sum(conv_specific$p < 0.1)
```

**Table 2. Number of channels significantly tracking the stimuli** 

<!-- | | same talker | different talker | meaningful | nonsense | general constraint | specific constraint | -->
<!-- | --- | --- | --- | --- | --- | --- | --- | -->
<!-- | cross correlation | `r xcorr_same_talker_nchans` | `r xcorr_diff_talker_nchans` | `r xcorr_meaningful_nchans` | `r xcorr_nonsense_nchans` |  `r xcorr_general_nchans` | `r xcorr_specific_nchans` | -->
<!-- | convolution | `r conv_same_talker_nchans` | `r conv_diff_talker_nchans` | `r conv_meaningful_nchans` | `r conv_nonsense_nchans` |  `r conv_general_nchans` | `r conv_specific_nchans` | -->

**Output 3. Sample of channels with significant cross-correlation with stimulus waveform under the same-talker condition ($\alpha$ < 0.1)**
```{r}
# xcorr_same_talker[which(xcorr_same_talker$p < 0.1),]
```

**Output 4. Sample of channels with significant convolution with stimulus waveform under the same-talker condition ($\alpha$ < 0.1)**
```{r}
# conv_same_talker[which(conv_same_talker$p < 0.1),]
```


