---
title: "Talker change data processing"
author: "Letitia Ho"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document: default
---

```{r setup, include=FALSE}
require("knitr")
library("dplyr")
library("kableExtra")
```

```{r FUNCTIONS, warning=FALSE, include=FALSE}
# Function for subsetting data based on condition and level
subset_by_condition <- function(data, condition) {
  channel_columns = paste("X", 1:128, sep = "")
  if (condition == "talker") {
    S <- filter(data, talker == "S") %>% select(all_of(channel_columns))
    T <- filter(data, talker == "T") %>% select(all_of(channel_columns))
    return(list(S = S, T = T))
  } else if (condition == "meaning") {
    M <- filter(data, meaning == "M") %>% select(all_of(channel_columns))
    N <- filter(data, meaning == "N") %>% select(all_of(channel_columns))
    return(list(M = M, N = N))
  } else if (condition == "constraint") {
    S <- filter(data, constraint == "S") %>% select(all_of(channel_columns))
    G <- filter(data, constraint == "G") %>% select(all_of(channel_columns))
    return(list(S = S, G = G))
  }
}

# Function for subsetting data based on formant
subset_by_formant <- function(data, formants) {
  if (formants == "f0") {
    data <- filter(data, formant == "f0")
  } else if (formants == "f1_f2") {
    data <- filter(data, formant == "f1_f2") 
  } else if (formants == "f3") {
    data <- filter(data, formant == "f3")
  }
  return(data)
}

# Function for running a one-sample t-test and saving the p-value, t-statistic, and df
get_one_sample_t <- function(data) {
  t <- apply(data, MARGIN = 2, function(channel) {t.test(channel)$statistic})
  df <- apply(data, MARGIN = 2, function(channel) {t.test(channel)$parameter})
  p <- apply(data, MARGIN = 2, function(channel) {t.test(channel)$p.value})
  return(data.frame("t" = t, "df" = df, "p" = p))
}

# Function for running a paired-samples t-test and saving the p-value, t-statistic, and df
get_paired_samples_t <- function(group1, group2) {
  t <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$statistic}, group1, group2)
  df <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$parameter}, group1, group2)
  p <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$p.value}, group1, group2)
  return(data.frame("t" = t, "df" = df, "p" = p))
  }

# Function for running an independent-samples t-test and saving the p-value, t-statistic, and df
get_ind_samples_t <- function(group1, group2) { # mostly to replicate JAMOVI t-test results
  t <- mapply(function(x, y) {t.test(x, y, paired = FALSE, var.equal = TRUE)$statistic},
              group1, group2)
  df <- mapply(function(x, y) {t.test(x, y, paired = FALSE, var.equal = TRUE)$parameter}, 
               group1, group2)
  p <- mapply(function(x, y) {t.test(x, y, paired = FALSE, var.equal = TRUE)$p.value}, 
              group1, group2)
  return(data.frame("t" = t, "df" = df, "p" = p))
}

# Taking the p-values of the t-test results and assigning a 1 if sig, 0 if not
get_hot <- function(data) {
  hot <- c()
  hot[data$p < 0.1] <- 1
  hot[data$p > 0.1] <- 0
  return(hot)
}

# Comparing two hot vectors and assigning a 1 if the values match, 0 if not
get_match <- function(group1, group2) {
  match <- c()
  match <- ifelse(group1 == 1 & group2 == 1, 1, 0)
  return(match)
}
```

```{r create_data_tables_for_display, warning=FALSE, include=FALSE}
# Get a single frequency table for results of the t-tests
get_frequency_table <- function(data) {
    hot <- get_hot(data)
    counts <- margin.table(table(hot), 1)
    proportions <- prop.table(table(hot))
    if (dim(counts) == 1) {return(data.frame("counts" = c(counts[1], 0), "proportion" = c(proportions[1], 0)))}
    else {return(data.frame("counts" = c(counts[1], counts[2]), "proportion" = c(proportions[1], proportions[2])))}
  }

# Get a frequency table that combines results for xcorr and conv
get_combined_frequency_table <- function(xcorr, conv, title = NULL) {
  xcorr_freqs <- get_frequency_table(xcorr)
  conv_freqs <- get_frequency_table(conv)
  kable(cbind(xcorr_freqs, conv_freqs), caption = title) %>%
    kable_styling(c("striped", "condensed"), full_width = F) %>%
    add_header_above(c(" ", "Cross-correlation" = 2, "Convolution" = 2))
}

# Get a frequency table that combines results for the three formant levels
get_formant_frequency_table <- function(f0, f1_f2, f3, title = NULL) {
  f0_freqs <- get_frequency_table(f0)
  f1_f2_freqs <- get_frequency_table(f1_f2)
  f3_freqs <- get_frequency_table(f3)
  kable(cbind(f0_freqs, f1_f2_freqs, f3_freqs), caption = title) %>%
    kable_styling(c("striped", "condensed"), full_width = F) %>%
    add_header_above(c(" ", "F0" = 2, "F1 + F2" = 2, "F3" = 2))
}
```

``` {r load_data, warning=FALSE, include=FALSE}
# Read files
setwd("/Applications/eeglab2019/talker-change-data-processing/")
xcorr <- read.csv("data/aggregate/cross_correlation_data.csv")
conv <- read.csv("data/aggregate/convolution_data.csv")
xcorr_formants <- read.csv("data/aggregate/cross_correlation_formant_data.csv")

# Save channel numbers
channels <- as.character(1:128)
channel_columns <- paste("X", 1:128, sep = "")

# Subset by condition for easy access
xcorr_talker <- subset_by_condition(xcorr, "talker")
xcorr_meaning <- subset_by_condition(xcorr, "meaning")
xcorr_constraint <- subset_by_condition(xcorr, "constraint")
conv_talker <- subset_by_condition(conv, "talker")
conv_meaning <- subset_by_condition(conv, "meaning")
conv_constraint <- subset_by_condition(conv, "constraint")
conv <- select(conv, all_of(channel_columns))
xcorr <- select(xcorr, all_of(channel_columns))

# Subset by formants for easy access
f0 <- subset_by_formant(xcorr_formants, "f0")
f1_f2 <- subset_by_formant(xcorr_formants, "f1_f2")
f3 <- subset_by_formant(xcorr_formants, "f3")

# Subset formant data by condition for easy access
f0_talker <- subset_by_condition(f0, "talker")
f0_meaning <- subset_by_condition(f0, "meaning")
f0_constraint <- subset_by_condition(f0, "constraint")
f1_f2_talker <- subset_by_condition(f1_f2, "talker")
f1_f2_meaning <- subset_by_condition(f1_f2, "meaning")
f1_f2_constraint <- subset_by_condition(f1_f2, "constraint")
f3_talker <- subset_by_condition(f3, "talker")
f3_meaning <- subset_by_condition(f3, "meaning")
f3_constraint <- subset_by_condition(f3, "constraint")
```




******

#### 1. Do cortical regions track temporal variation in the speech signal?

``` {r, echo=FALSE}
# One-sample t-test for the cross-correlation values for each channel
t_xcorr <- get_one_sample_t(xcorr)
# One-sample t-test for the convolution values for each channel
t_conv <- get_one_sample_t(conv)
# Create a frequency table with the results
get_combined_frequency_table(t_xcorr, t_conv, title = "Table 1. Channels significantly tracking the stimuli")
```

**Output 1. Channels with significant cross-correlation with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the cross-correlation of each stimulus waveform with each electrode EEG trace across all conditions.

```{r, echo=FALSE}
# Printing the t-test results for significant electrodes
t_xcorr[which(t_xcorr$p < 0.1),]
```

**Output 2. Channels with significant convolution with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the convolution of each stimulus waveform with each electrode EEG trace across all conditions.

```{r, echo=FALSE}
# Printing the t-test results for significant electrodes
t_conv[which(t_conv$p < 0.1),]
```




************

#### 2. Do cortical regions track differently depending on the conditions?

Tested by one-sample t-tests for significant waveform tracking in each level of each condition.

**Channels significantly tracking the stimuli in the talker condition ($\alpha$ < 0.1)** 

```{r, echo=FALSE}
# One-sample t-tests over each electrode for the same talker condition
t_xcorr_talker_s <- get_one_sample_t(xcorr_talker$S)
t_conv_talker_s <- get_one_sample_t(conv_talker$S)
get_combined_frequency_table(t_xcorr_talker_s, t_conv_talker_s, title = "Table 2. Same talker")
# One-sample t-tests over each electrode for the different talker condition
t_xcorr_talker_t <- get_one_sample_t(xcorr_talker$T)
t_conv_talker_t <- get_one_sample_t(conv_talker$T)
get_combined_frequency_table(t_xcorr_talker_t, t_conv_talker_t, title = "Table 3. Different talker")
```

**Channels significantly tracking the stimuli in the meaning condition ($\alpha$ < 0.1)** 

```{r, echo=FALSE}
# One-sample t-tests over each electrode for the meaning condition
t_xcorr_meaning_m <- get_one_sample_t(xcorr_meaning$M)
t_conv_meaning_m <- get_one_sample_t(conv_meaning$M)
get_combined_frequency_table(t_xcorr_meaning_m, t_conv_meaning_m, title = "Table 4. Meaningful")
# One-sample t-tests over each electrode for the nonsense condition
t_xcorr_meaning_n <- get_one_sample_t(xcorr_meaning$N)
t_conv_meaning_n <- get_one_sample_t(conv_meaning$N)
get_combined_frequency_table(t_xcorr_meaning_n, t_conv_meaning_n, title = "Table 5. Nonsense")
```

**Channels significantly tracking the stimuli in the constraint condition ($\alpha$ < 0.1)** 

```{r, echo=FALSE}
# One-sample t-tests over each electrode for the high constraint condition
t_xcorr_constraint_s <- get_one_sample_t(xcorr_constraint$S)
t_conv_constraint_s <- get_one_sample_t(conv_constraint$S)
get_combined_frequency_table(t_xcorr_constraint_s, t_conv_constraint_s, title = "Table 6. High constraint")
# One-sample t-tests over each electrode for the low constraint condition
t_xcorr_constraint_g <- get_one_sample_t(xcorr_constraint$G)
t_conv_constraint_g <- get_one_sample_t(conv_constraint$G)
get_combined_frequency_table(t_xcorr_constraint_g, t_conv_constraint_g, title = "Table 7. Low constraint")
```




************

#### 3. Do cortical regions track the levels of each condition differently?

Tested by paired-samples t-tests between the two levels of each condition. I.e. a test of whether an electrode significantly distinguishes condition levels.

**Channels significantly distinguishing the stimuli in each condition ($\alpha$ < 0.1)** 

```{r, echo=FALSE}
# Paired t-tests for talker
t_xcorr_talker_paired <- get_paired_samples_t(xcorr_talker$S, xcorr_talker$T)
t_conv_talker_paired <- get_paired_samples_t(conv_talker$S, conv_talker$T)
get_combined_frequency_table(t_xcorr_talker_paired, t_conv_talker_paired, title = "Table 8. Talker")

# Paired t-tests for meaning
t_xcorr_meaning_paired <- get_paired_samples_t(xcorr_meaning$M, xcorr_meaning$N)
t_conv_meaning_paired <- get_paired_samples_t(conv_meaning$M, conv_meaning$N)
get_combined_frequency_table(t_xcorr_meaning_paired, t_conv_meaning_paired, title = "Table 9. Meaning")

# Paired t-tests for constraint
t_xcorr_constraint_paired <- get_paired_samples_t(xcorr_constraint$S, xcorr_constraint$G)
t_conv_constraint_paired <- get_paired_samples_t(conv_constraint$S, conv_constraint$G)
get_combined_frequency_table(t_xcorr_constraint_paired, t_conv_constraint_paired, title = "Table 10. Constraint")
```


**Table 11. *p*-values for each level in each condition ($\alpha$ < 0.1, )**

```{r, warning=FALSE, echo=FALSE}
# Creating a table to display all the p-values
spacer <- matrix(" ", 128, 1)
level_p_values <- data.frame(channels, 
                     t_xcorr_talker_s$p,
                     t_xcorr_talker_t$p, 
                     t_xcorr_talker_paired$p,
                     spacer,
                     t_xcorr_meaning_m$p,
                     t_xcorr_meaning_n$p, 
                     t_xcorr_meaning_paired$p,
                     spacer,
                     t_xcorr_constraint_s$p,
                     t_xcorr_constraint_g$p,
                     t_xcorr_constraint_paired$p)  %>%
  mutate_if(is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, NULL),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

# kable(level_p_values)
kable(level_p_values, escape = F, col.names = c("Channel", "S", "T", "Paired", "---",
                                                "M", "N", "Paired", "---",
                                                "S", "G", "Paired")) %>%
  add_header_above(c(" " = 1, "Talker" = 3, " "  = 1, "Meaning" = 3, " " = 1, "Constraint" = 3)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

**Table 12. Channels that distinguish between levels in a condition ($\alpha$ < 0.1)** The *condition diff* column contains channels that significantly distinguish between the two levels in a condition. The *match x* columns for individual levels indicate channels that significantly track the stimuli in the condition level. The *match both* column indicates channels that both distinguish between levels and significantly track stimuli under both levels. Differences between the *match x* columns in each condition show differences between the networks tracking speech under each condition level.

```{r, echo=FALSE, include=TRUE}
# Creating a table to display all the channels that are significant for each condition level
talker_diff <- get_hot(t_xcorr_talker_paired)
talker_s_match <- get_match(talker_diff, get_hot(t_xcorr_talker_s))
talker_t_match <- get_match(talker_diff, get_hot(t_xcorr_talker_t))
talker_both_match <- get_match(talker_s_match, talker_t_match)

meaning_diff <- get_hot(t_xcorr_meaning_paired)
meaning_m_match <- get_match(meaning_diff, get_hot(t_xcorr_meaning_m))
meaning_n_match <- get_match(meaning_diff, get_hot(t_xcorr_meaning_n))
meaning_both_match <- get_match(meaning_m_match, meaning_n_match)

constraint_diff <- get_hot(t_xcorr_constraint_paired)
constraint_s_match <- get_match(constraint_diff, get_hot(t_xcorr_constraint_s))
constraint_g_match <- get_match(constraint_diff, get_hot(t_xcorr_constraint_g))
constraint_both_match <- get_match(constraint_s_match, constraint_g_match)

match_table <- data.frame(channels, 
                          talker_s_match, talker_t_match, talker_diff, talker_both_match,
                          meaning_m_match, meaning_n_match, meaning_diff, meaning_both_match,
                          constraint_s_match, constraint_g_match, constraint_diff, constraint_both_match) %>%
  mutate_if(is.numeric, function(x) {ifelse(x == 1, 
                                            cell_spec(x, background = "tomato"), 
                                            cell_spec(x, NULL))})

kable(match_table, escape = F, col.names = c("Channel", 
                                             "match s", "match t", "diff", "match both",
                                             "match m", "match n", "diff", "match both",
                                             "match s", "match g", "diff", "match both"))  %>%
  add_header_above(c(" " = 1, "Talker" = 4, "Meaning" = 4, "Constraint" = 4)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

**Table 13. Number of conditions that distinguish by each channel ($\alpha$ < 0.1)**

```{r, echo=FALSE}
# Creating a table to display all the channels that are significant for two condition levels
total <- cbind(talker_diff, meaning_diff, constraint_diff) %>% apply(MARGIN = 1, sum)
counts <- margin.table(table(total), 1)
proportions <- prop.table(table(total))
df <- data.frame("counts" = c(counts[1], counts[2], counts[3]), "proportion" = c(proportions[1], proportions[2], proportions[3]))
row.names(df) <- c("No conditions", "One condition", "Two conditions")
kable(df) %>% kable_styling(c("striped", "condensed"), full_width = F)
```




************

#### 4. Are the brain organizations different in different conditions related to tracking?




************

#### 5. What properties are being tracked in the meaning and talker conditions?

Tested by one-sample t-tests for significant waveform tracking in each level of each condition for each subband.

**Table 1. Proportion of significantly tracking channels**

``` {r, include=FALSE}
# Run one-sample t-tests for each condition level for each formant
t_f0_talker_s <- get_one_sample_t(f0_talker$S)
t_f1_f2_talker_s <- get_one_sample_t(f1_f2_talker$S)
t_f3_talker_s <- get_one_sample_t(f3_talker$S)
t_f0_talker_t <- get_one_sample_t(f0_talker$T)
t_f1_f2_talker_t <- get_one_sample_t(f1_f2_talker$T)
t_f3_talker_t <- get_one_sample_t(f3_talker$T)
t_f0_meaning_m <- get_one_sample_t(f0_meaning$M)
t_f1_f2_meaning_m <- get_one_sample_t(f1_f2_meaning$M)
t_f3_meaning_m <- get_one_sample_t(f3_meaning$M)
t_f0_meaning_n <- get_one_sample_t(f0_meaning$N)
t_f1_f2_meaning_n <- get_one_sample_t(f1_f2_meaning$N)
t_f3_meaning_n <- get_one_sample_t(f3_meaning$N)
t_f0_constraint_s <- get_one_sample_t(f0_constraint$S)
t_f1_f2_constraint_s <- get_one_sample_t(f1_f2_constraint$S)
t_f3_constraint_s <- get_one_sample_t(f3_constraint$S)
t_f0_constraint_g <- get_one_sample_t(f0_constraint$G)
t_f1_f2_constraint_g <- get_one_sample_t(f1_f2_constraint$G)
t_f3_constraint_g <- get_one_sample_t(f3_constraint$G)
```

```{r, echo=FALSE}
# Create a frequency table displaying the proportion of significant channels for each level
talker_s <- c(get_frequency_table(t_f0_talker_s)[2,2], 
              get_frequency_table(t_f1_f2_talker_s)[2,2], 
              get_frequency_table(t_f3_talker_s)[2,2])
talker_t <- c(get_frequency_table(t_f0_talker_t)[2,2], 
              get_frequency_table(t_f1_f2_talker_t)[2,2], 
              get_frequency_table(t_f3_talker_t)[2,2])
meaning_m <- c(get_frequency_table(t_f0_meaning_m)[2,2], 
              get_frequency_table(t_f1_f2_meaning_m)[2,2], 
              get_frequency_table(t_f3_meaning_m)[2,2])
meaning_n <- c(get_frequency_table(t_f0_meaning_n)[2,2], 
              get_frequency_table(t_f1_f2_meaning_n)[2,2], 
              get_frequency_table(t_f3_meaning_n)[2,2])
constraint_s <-c(get_frequency_table(t_f0_constraint_s)[2,2], 
              0, 
              get_frequency_table(t_f3_constraint_s)[2,2])
constraint_g <-c(get_frequency_table(t_f0_constraint_g)[2,2], 
              get_frequency_table(t_f1_f2_constraint_g)[2,2], 
              get_frequency_table(t_f3_constraint_g)[2,2])

df <- as.data.frame(rbind(talker_s, talker_t, meaning_m, meaning_n, constraint_s, constraint_g)) %>%
  mutate_if(is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {cell_spec(x, background = spec_color(x, begin = 0.5, direction = -1, scale = c(0, 0.5)))})
row.names(df) <- c("Same talker", "Different talker", "Meaningful", "Nonsense", "High constraint", "Low constraint")
# always specify scale or else it scales by column
kable(df, escape = F, col.names = c("F0", "F1 + F2", "F3")) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

**Table 2. Channels significantly tracking the stimuli in the talker condition** 

```{r, warning=FALSE, echo=FALSE}
get_formant_frequency_table(t_f0_talker_s, t_f1_f2_talker_s, t_f3_talker_s, title = "Same talker")
get_formant_frequency_table(t_f0_talker_t, t_f1_f2_talker_t, t_f3_talker_t, title = "Different talker")
```

**Table 3. Channels significantly tracking the stimuli in the meaning condition** 

```{r, warning=FALSE, echo=FALSE}
get_formant_frequency_table(t_f0_meaning_m, t_f1_f2_meaning_m, t_f3_meaning_m, title = "Meaningful")
get_formant_frequency_table(t_f0_meaning_n, t_f1_f2_meaning_n, t_f3_meaning_n, title = "Nonsense")
```

**Table 4. Channels significantly tracking the stimuli in the constraint condition** 

```{r, warning=FALSE, echo=FALSE}
get_formant_frequency_table(t_f0_constraint_s, t_f1_f2_constraint_s, t_f3_constraint_s, title = "High constraint")
get_formant_frequency_table(t_f0_constraint_g, t_f1_f2_constraint_g, t_f3_constraint_g, title = "Low constraint")
```

