---
title: "Talker change data processing"
author: "Letitia Ho"
date: "8/12/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
require("knitr")
library("dplyr")
library("kableExtra")
```

``` {r load_data, warning=FALSE, include=FALSE}
# Read files
setwd("/Applications/eeglab2019/talker-change-data-processing/")
xcorr <- read.csv("data/aggregate/cross_correlation_data.csv")
conv <- read.csv("data/aggregate/convolution_data.csv")
xcorr_formants <- read.csv("data/aggregate/cross_correlation_formant_data.csv")
conv_formants <- read.csv("data/aggregate/convolution_formant_data.csv")

# Function for subsetting data based on condition and level
subset <- function(data, condition) {
  channel_columns = paste("X", 1:128, sep = "")
  if (condition == "talker") {
    S <- filter(data, talker == "S") %>% select(all_of(channel_columns))
    T <- filter(data, talker == "T") %>% select(all_of(channel_columns))
    return(list(S = S, T = T))
  } else if (condition == "meaning") {
    M <- filter(data, meaning == "M") %>% select(all_of(channel_columns))
    N <- filter(data, meaning == "N") %>% select(all_of(channel_columns))
    return(list(M = M, N = N))
  } else if (condition == "constraint") {
    S <- filter(data, constraint == "S") %>% select(all_of(channel_columns))
    G <- filter(data, constraint == "G") %>% select(all_of(channel_columns))
    return(list(S = S, G = G))
  }
}
# Channel numbers
channels <- as.character(1:128)
channel_columns <- paste("X", 1:128, sep = "")

# Subset data for easy access
xcorr_talker <- subset(xcorr, "talker")
xcorr_meaning <- subset(xcorr, "meaning")
xcorr_constraint <- subset(xcorr, "constraint")
conv_talker <- subset(conv, "talker")
conv_meaning <- subset(conv, "meaning")
conv_constraint <- subset(conv, "constraint")
conv <- select(conv, all_of(channel_columns))
xcorr <- select(xcorr, all_of(channel_columns))
```

```{r functions, warning=FALSE, include=FALSE}
get_one_sample_t <- function(data) {
  t <- apply(data, MARGIN = 2, function(channel) {t.test(channel)$statistic})
  df <- apply(data, MARGIN = 2, function(channel) {t.test(channel)$parameter})
  p <- apply(data, MARGIN = 2, function(channel) {t.test(channel)$p.value})
  return(data.frame("t" = t, "df" = df, "p" = p))
}

get_paired_samples_t <- function(group1, group2) {
  t <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$statistic}, group1, group2)
  df <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$parameter}, group1, group2)
  p <- mapply(function(x, y) {t.test(x, y, paired = TRUE)$p.value}, group1, group2)
  return(data.frame("t" = t, "df" = df, "p" = p))
  }

get_ind_samples_t <- function(group1, group2) { # mostly to replicate JAMOVI t-test results
  t <- mapply(function(x, y) {t.test(x, y, paired = FALSE, var.equal = TRUE)$statistic},
              group1, group2)
  df <- mapply(function(x, y) {t.test(x, y, paired = FALSE, var.equal = TRUE)$parameter}, 
               group1, group2)
  p <- mapply(function(x, y) {t.test(x, y, paired = FALSE, var.equal = TRUE)$p.value}, 
              group1, group2)
  return(data.frame("t" = t, "df" = df, "p" = p))
}

get_hot <- function(data) {
  hot <- c()
  hot[data$p < 0.1] <- 1
  hot[data$p > 0.1] <- 0
  return(hot)
}

get_match <- function(group1, group2) {
  match <- c()
  match <- ifelse(group1 == 1 & group2 == 1, 1, 0)
  return(match)
}
```

```{r plot_graphs_and_tables, warning=FALSE, include=FALSE}
get_frequency_table <- function(data) {
    hot <- get_hot(data)
    counts <- margin.table(table(hot), 1)
    proportions <- prop.table(table(hot))
    return(data.frame("counts" = c(counts[1], counts[2]), "proportion" = c(proportions[1], proportions[2])))
  }

get_combined_frequency_table <- function(xcorr, conv, title = NULL) {
  xcorr_freqs <- get_frequency_table(xcorr)
  conv_freqs <- get_frequency_table(conv)
  kable(cbind(xcorr_freqs, conv_freqs), caption = title) %>%
    kable_styling(c("striped", "condensed"), full_width = F) %>%
    add_header_above(c(" ", "Cross-correlation" = 2, "Convolution" = 2))
}
```


******

#### 1. Do cortical regions track temporal variation in the speech signal?

``` {r, echo=FALSE}
t_xcorr <- get_one_sample_t(xcorr)
t_conv <- get_one_sample_t(conv)
get_combined_frequency_table(t_xcorr, t_conv, title = "Table 1. Channels significantly tracking the stimuli")
```

**Output 1. Channels with significant cross-correlation with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the cross-correlation of each stimulus waveform with each electrode EEG trace across all conditions.

```{r, echo=FALSE}
t_xcorr[which(t_xcorr$p < 0.1),]
```

**Output 2. Channels with significant convolution with stimulus waveform ($\alpha$ < 0.1)** Computed with a one-sample t-test for the convolution of each stimulus waveform with each electrode EEG trace across all conditions.

```{r, echo=FALSE}
t_conv[which(t_conv$p < 0.1),]
```

************

#### 2. Do cortical regions track differently depending on the conditions?

Tested by one-sample t-tests for significant waveform tracking in each level of each condition.

**Channels significantly tracking the stimuli in the talker condition** 

```{r, echo=FALSE}
t_xcorr_talker_s <- get_one_sample_t(xcorr_talker$S)
t_conv_talker_s <- get_one_sample_t(conv_talker$S)
get_combined_frequency_table(t_xcorr_talker_s, t_conv_talker_s, title = "Table 2. Same talker")
t_xcorr_talker_t <- get_one_sample_t(xcorr_talker$T)
t_conv_talker_t <- get_one_sample_t(conv_talker$T)
get_combined_frequency_table(t_xcorr_talker_t, t_conv_talker_t, title = "Table 3. Different talker")
```

**Channels significantly tracking the stimuli in the meaning condition** 

```{r, echo=FALSE}
t_xcorr_meaning_m <- get_one_sample_t(xcorr_meaning$M)
t_conv_meaning_m <- get_one_sample_t(conv_meaning$M)
get_combined_frequency_table(t_xcorr_meaning_m, t_conv_meaning_m, title = "Table 4. Meaningful")
t_xcorr_meaning_n <- get_one_sample_t(xcorr_meaning$N)
t_conv_meaning_n <- get_one_sample_t(conv_meaning$N)
get_combined_frequency_table(t_xcorr_meaning_n, t_conv_meaning_n, title = "Table 5. Nonsense")
```

**Channels significantly tracking the stimuli in the constraint condition** 

```{r, echo=FALSE}
t_xcorr_constraint_s <- get_one_sample_t(xcorr_constraint$S)
t_conv_constraint_s <- get_one_sample_t(conv_constraint$S)
get_combined_frequency_table(t_xcorr_constraint_s, t_conv_constraint_s, title = "Table 6. High constraint")
t_xcorr_constraint_g <- get_one_sample_t(xcorr_constraint$G)
t_conv_constraint_g <- get_one_sample_t(conv_constraint$G)
get_combined_frequency_table(t_xcorr_constraint_g, t_conv_constraint_g, title = "Table 7. Low constraint")
```

************

#### 3. Do cortical regions track the levels of each condition differently?

Tested by paired-samples t-tests between the two levels of each condition. I.e. a test of whether an electrode significantly distinguishes condition levels.

**Channels significantly distinguishing the stimuli in each condition** 

```{r, echo=FALSE}
# Talker
t_xcorr_talker_paired <- get_paired_samples_t(xcorr_talker$S, xcorr_talker$T)
t_conv_talker_paired <- get_paired_samples_t(conv_talker$S, conv_talker$T)
get_combined_frequency_table(t_xcorr_talker_paired, t_conv_talker_paired, title = "Table 9. Talker")

# Meaning
t_xcorr_meaning_paired <- get_paired_samples_t(xcorr_meaning$M, xcorr_meaning$N)
t_conv_meaning_paired <- get_paired_samples_t(conv_meaning$M, conv_meaning$N)
get_combined_frequency_table(t_xcorr_meaning_paired, t_conv_meaning_paired, title = "Table 10. Meaning")

# Constraint
t_xcorr_constraint_paired <- get_paired_samples_t(xcorr_constraint$S, xcorr_constraint$G)
t_conv_constraint_paired <- get_paired_samples_t(conv_constraint$S, conv_constraint$G)
get_combined_frequency_table(t_xcorr_constraint_paired, t_conv_constraint_paired, title = "Table 11. Constraint")
```


**Table 8. *p*-values for each level in each condition**

```{r, warning=FALSE, echo=FALSE}
spacer <- matrix(" ", 128, 1)
level_p_values <- data.frame(channels, 
                     t_xcorr_talker_s$p,
                     t_xcorr_talker_t$p, 
                     t_xcorr_talker_paired$p,
                     spacer,
                     t_xcorr_meaning_m$p,
                     t_xcorr_meaning_n$p, 
                     t_xcorr_meaning_paired$p,
                     spacer,
                     t_xcorr_constraint_s$p,
                     t_xcorr_constraint_g$p,
                     t_xcorr_constraint_paired$p)  %>%
  mutate_if(is.numeric, function(x) {round(x, digits = 3)}) %>%
  mutate_if(is.numeric, function(x) {ifelse(x > 0.1, 
                                            cell_spec(x, bold = F, color = "black"),
                                            cell_spec(x, background = spec_color(x, 
                                                                                 direction = 1, 
                                                                                 begin = 0.65, 
                                                                                 end = 1, 
                                                                                 option = "B", 
                                                                                 scale_from = c(0,0.1))))})

# kable(level_p_values)
kable(level_p_values, escape = F, col.names = c("Channel", "S", "T", "Paired", "---librar",
                                                "M", "N", "Paired", "---",
                                                "S", "G", "Paired")) %>%
  add_header_above(c(" " = 1, "Talker" = 3, " "  = 1, "Meaning" = 3, " " = 1, "Constraint" = 3)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r, warning=FALSE, include=FALSE}
# level_p_values <- data.frame(channels, 
#                      t_xcorr_talker_s$p, t_conv_talker_s$p, 
#                      t_xcorr_talker_t$p, t_conv_talker_t$p,
#                      t_xcorr_talker_paired$p, t_conv_talker_paired$p,
#                      t_xcorr_meaning_m$p, t_conv_meaning_m$p,
#                      t_xcorr_meaning_n$p, t_conv_meaning_n$p,
#                      t_xcorr_meaning_paired$p, t_conv_meaning_paired$p,
#                      t_xcorr_constraint_s$p, t_conv_constraint_s$p,
#                      t_xcorr_constraint_g$p, t_conv_constraint_g$p,
#                      t_xcorr_constraint_paired$p, t_conv_constraint_paired$p)  %>%
#   mutate_if(is.numeric, function(x) {round(x, digits = 3)}) %>%
#   mutate_if(is.numeric, function(x) {ifelse(x < 0.1, cell_spec(x, bold = F, color = spec_color(x, direction = -1)),
#     cell_spec(x, bold = F, color = "black"))})

# names <- c()
# names[1:2:18] <- c("XCorr", "Conv")
# kable(level_p_values, escape = F, col.names = c("Channel", names))  %>%
#   add_header_above(c(" " = 1, "Same talker" = 2, "Different talker" = 2, "Paired" = 2,
#                      "Meaningful" = 2, "Nonsense" = 2, "Paired" = 2,
#                      "High constraint" = 2, "Low constraint" = 2,  "Paired" = 2)) %>%
#   kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

**Table 13. Channels that distinguish between levels in a condition** The *condition diff* column contains channels that significantly distinguish between the two levels in a condition. The *match x* columns for individual levels indicate channels that significantly track the stimuli in the condition level. The *match both* column indicates channels that both distinguish between levels and significantly track stimuli under both levels. Differences between the *match x* columns in each condition show differences between the networks tracking speech under each condition level.

```{r, echo=FALSE}
# Match columns based on cross-correlation only
talker_diff <- get_hot(t_xcorr_talker_paired)
talker_s_match <- get_match(talker_diff, get_hot(t_xcorr_talker_s))
talker_t_match <- get_match(talker_diff, get_hot(t_xcorr_talker_t))
talker_both_match <- get_match(talker_s_match, talker_t_match)

meaning_diff <- get_hot(t_xcorr_meaning_paired)
meaning_m_match <- get_match(meaning_diff, get_hot(t_xcorr_meaning_m))
meaning_n_match <- get_match(meaning_diff, get_hot(t_xcorr_meaning_n))
meaning_both_match <- get_match(meaning_m_match, meaning_n_match)

constraint_diff <- get_hot(t_xcorr_constraint_paired)
constraint_s_match <- get_match(constraint_diff, get_hot(t_xcorr_constraint_s))
constraint_g_match <- get_match(constraint_diff, get_hot(t_xcorr_constraint_g))
constraint_both_match <- get_match(constraint_s_match, constraint_g_match)

match_table <- data.frame(channels, 
                          talker_s_match, talker_t_match, talker_diff, talker_both_match,
                          meaning_m_match, meaning_n_match, meaning_diff, meaning_both_match,
                          constraint_s_match, constraint_g_match, constraint_diff, constraint_both_match) %>%
  mutate_if(is.numeric, function(x) {ifelse(x == 1, 
                                            cell_spec(x, color = "tomato3"), 
                                            cell_spec(x, bold = F, color = "black"))})

kable(match_table, align = "c", escape = F, col.names = c("Channel", 
                                                          "match s", "match t", "diff", "match both",
                                                          "match m", "match n", "diff", "match both",
                                                          "match s", "match g", "diff", "match both"))  %>%
  add_header_above(c(" " = 1, "Talker" = 4, "Meaning" = 4, "Constraint" = 4)) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

************

#### 4. Are the brain organizations different in different conditions related to tracking?

Tested by 

**Subheading** 

************

#### 5. What properties are being tracked in the meaning and talker conditions?

Tested by 

**Subheading** 

```{r, warning=FALSE, echo=FALSE, include=FALSE}
get_channel_means <- function(data, condition) {
  channel_columns = paste("X", 1:128, sep = "")
  if (condition == "talker") {channel_means <- group_by(data, talker) %>% 
                              summarise(across(channel_columns, mean))}
  if (condition == "meaning") {channel_means <- group_by(data, meaning) %>% 
                              summarise(across(channel_columns, mean))}
  if (condition == "constraint") {channel_means <- group_by(data, constraint) %>% 
                                  summarise(across(channel_columns, mean))}
  return(channel_means)
}

# Talker
talker_f0 <- get_channel_means(filter(xcorr_formants, formant == "f0"), condition = "talker")
talker_f1_f2 <- get_channel_means(filter(xcorr_formants, formant == "f1_f2"), condition = "talker")
talker_f3 <- get_channel_means(filter(xcorr_formants, formant == "f3"), condition = "talker")

# Meaning
meaning_f0 <- get_channel_means(filter(xcorr_formants, formant == "f0"), condition = "meaning")
meaning_f1_f2 <- get_channel_means(filter(xcorr_formants, formant == "f1_f2"), condition = "meaning")
meaning_f3 <- get_channel_means(filter(xcorr_formants, formant == "f3"), condition = "meaning")

# Constraint
constraint_f0 <- get_channel_means(filter(xcorr_formants, formant == "f0"), condition = "constraint")
constraint_f1_f2 <- get_channel_means(filter(xcorr_formants, formant == "f1_f2"), condition = "constraint")
constraint_f3 <- get_channel_means(filter(xcorr_formants, formant == "f3"), condition = "constraint")
```

```{r, include=FALSE}
t.test(t(talker_f0[1,2:128]), t(talker_f0[2,2:128]), paired = TRUE)
```



